---
title: "Descriptives of Caregiver Speech - Automated LENA values"
author: "Janet Bang"
date: "November 17, 2022"
output:
  html_document: 
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This code is for the LENA data in the manuscript.


# Load libraries and set theme
```{r}
library(tidyverse)
library(ppcor)
library(gridExtra)
library(psych)

theme_set(theme_bw())
```



# Prep data
## Read in data
```{r}
# lena all-day talk
lena_allday <- read_csv("./data_demo_lena_transcripts/lena.csv") %>% 
  mutate(id = factor(id), 
         language = factor(language))

str(lena_allday)


# create two dfs for plots
lena_allday_en <- lena_allday %>% filter(language == "english")
lena_allday_sp <- lena_allday %>% filter(language == "spanish")



# lena - 10 min segments
lena_10min <- read_csv("./data_demo_lena_transcripts/lena_10min.csv") %>% 
  mutate(id = factor(id), 
         language = factor(language))

str(lena_10min)


# create two dfs for plots
lena_10min_en <- lena_10min %>% filter(language == "english")
lena_10min_sp <- lena_10min %>% filter(language == "spanish")
```


## Duration of 10-min segments
```{r}
# English
mean(lena_10min_en$Dur10minval)/60
median(lena_10min_en$Dur10minval)/60
sd(lena_10min_en$Dur10minval)/60
min(lena_10min_en$Dur10minval)/60
max(lena_10min_en$Dur10minval)/60

# Spanish
mean(lena_10min_sp$Dur10minval)/60
median(lena_10min_sp$Dur10minval)/60
sd(lena_10min_sp$Dur10minval)/60
min(lena_10min_sp$Dur10minval)/60
max(lena_10min_sp$Dur10minval)/60
```



# Descriptives of percent of 10 min segments in each language
```{r}
lena_10min_en %>% 
  count(Dur10minval) %>% 
  mutate(prop = round(n/sum(n), 4)) %>% 
  arrange(desc(prop))


lena_10min_sp %>% 
  count(Dur10minval) %>% 
  mutate(prop = round(n/sum(n), 4)) %>% 
  arrange(desc(prop))
```



## Create duration and AWC values for top hr
```{r}
tophr_en <- lena_10min_en %>% 
  mutate(id = factor(id)) %>% 
  group_by(id) %>% 
  mutate(dur_total_hr = sum(Dur10minval)/3600, 
         awc_total_hr = sum(AWCval)) %>% 
  distinct(id, dur_total_hr, awc_total_hr) %>% 
  mutate(awc_perhr_densest = awc_total_hr/dur_total_hr) %>% 
  dplyr::select(id, dur_total_hr, awc_perhr_densest) %>% 
  mutate(language = "english")


tophr_sp <- lena_10min_sp %>% 
  mutate(id = factor(id)) %>% 
  group_by(id) %>% 
  mutate(dur_total_hr = sum(Dur10minval)/3600, 
         awc_total_hr = sum(AWCval)) %>% 
  distinct(id, dur_total_hr, awc_total_hr) %>% 
  mutate(awc_perhr_densest = awc_total_hr/dur_total_hr) %>% 
  dplyr::select(id, dur_total_hr, awc_perhr_densest) %>% 
  mutate(language = "spanish")

tophr <- rbind(tophr_en, tophr_sp)

```



## Descriptives - Top Hour
```{r}
# duration
describeBy(tophr$dur_total_hr, tophr$language, mat = T, fast = T)

# awc/hr
describeBy(tophr$awc_perhr_densest, tophr$language, mat = T, fast = T)

# max/min ratio
max(tophr_en$awc_perhr_densest)/min(tophr_en$awc_perhr_densest)
max(tophr_sp$awc_perhr_densest)/min(tophr_sp$awc_perhr_densest)

```


## Descriptives - ALL DAY
```{r}
# awc/hr
describeBy(lena_allday$awc_perhr_cleaned, lena_allday$language, mat = T, fast = T)

# max/min ratio
# min value in spanish is 512, which is higher than the min value for top hour of tCDS, but all-day includes ODS, so it may be different [family with min value is diff for top hour vs. all-day]
max(lena_allday$awc_perhr_cleaned)/min(lena_allday$awc_perhr_cleaned)
max(lena_allday$awc_perhr_cleaned)/min(lena_allday$awc_perhr_cleaned) 

```



# ALL-DAY TALK
## AWC - ascending order plot per family
```{r}
# separate graphs for english and spanish - otherwise there are gaps in the x axis for id
awc1 <- ggplot(lena_allday_en, aes(x = reorder(id, awc_perhr_cleaned), y = awc_perhr_cleaned)) +
  geom_col(fill = "darkgrey") +
  scale_y_continuous(limits = c(0, 4400)) +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        # text = element_text(size=40),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(x = "Families with 2-year-old children", y = "AWC per hour")


awc2 <- ggplot(lena_allday_sp, aes(x = reorder(id, awc_perhr_cleaned), y = awc_perhr_cleaned)) +
  geom_col(fill = "darkgrey") +
  scale_y_continuous(limits = c(0, 4400)) +
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        # text = element_text(size=40),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  labs(x = "Families with 2-year-old children", y = "AWC per hour")

grid.arrange(awc1, awc2, ncol = 2)
```




# TOP HOUR
## AWC - ascending order plot per family
```{r}
awc1_top <- ggplot(tophr_en, aes(x = reorder(id, awc_perhr_densest), y = awc_perhr_densest)) + 
  geom_col(fill = "white", color = "black") + 
  scale_y_continuous(limits = c(0, 9000)) + 
  theme(legend.position = "none", 
        panel.grid.major = element_blank(),
        text = element_text(size=40),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) + 
  labs(x = "Families with 2-year-old children", y = "AWC per densest tCDS hour", title = "English")

# figure for paper
ggsave("./figures/awc_perdensehr_en.pdf", width = 16, height = 11, dpi = 300)


awc2_top <- ggplot(tophr_sp, aes(x = reorder(id, awc_perhr_densest), y = awc_perhr_densest)) + 
  geom_col(fill = "white", color = "black") + 
  scale_y_continuous(limits = c(0, 9000)) + 
  theme(legend.position = "none", 
        panel.grid.major = element_blank(),
        text = element_text(size=40),
        axis.text.x = element_blank(), 
        axis.ticks.x = element_blank()) + 
  labs(x = "Families with 2-year-old children", y = "AWC per densest tCDS hour", title = "Spanish")
# figure for paper
ggsave("./figures/awc_perdensehr_sp.pdf", width = 16, height = 11, dpi = 300)

awc1_top
awc2_top
```



# TOP HOUR vs. ALL DAY
## T-test
```{r}
# english
tophr_allday_en <- lena_allday_en %>% 
  full_join(tophr_en, by = "id")

t.test(tophr_allday_en$awc_perhr_cleaned, tophr_allday_en$awc_perhr_densest, paired = T)


# spanish
tophr_allday_sp <- lena_allday_sp %>% 
  full_join(tophr_sp, by = "id")

t.test(tophr_allday_sp$awc_perhr_cleaned, tophr_allday_sp$awc_perhr_densest, paired = T)



# check to see if English and Spanish are different
tophr_both <- rbind(tophr_allday_en, tophr_allday_sp)
t.test(tophr_both$uncleaned_lena_dur ~ tophr_both$language.y, paired = F)
t.test(tophr_both$cleaned_lena_dur ~ tophr_both$language.y, paired = F)

```


## Correlations
```{r}
# english
ggplot(tophr_allday_en, aes(awc_perhr_densest, awc_perhr_cleaned)) +
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_x_continuous(limits = c(200, 9000))+
  scale_y_continuous(limits = c(200, 4500))+
  # theme(text = element_text(size = 25)) + 
  labs(x = "AWC per hour - DENSEST tCDS Hour", y = "AWC per hour - ALL DAY", title = "English") + 
  annotate("text", x = 2000, y = 4000, label = "paste(r, \" = .74\")", parse = TRUE, size = 10) + 
  theme(text = element_text(size = 25))
ggsave("./figures/corr_tophr_allday_en.pdf", width = 10, height = 8)

cor.test(tophr_allday_en$awc_perhr_densest, tophr_allday_en$awc_perhr_cleaned)


# spanish
ggplot(tophr_allday_sp, aes(awc_perhr_densest, awc_perhr_cleaned)) + # .79
  geom_point() + 
  geom_smooth(method = "lm") + 
  scale_x_continuous(limits = c(200, 9000))+
  scale_y_continuous(limits = c(200, 4500))+
  # theme(text = element_text(size = 25)) + 
  labs(x = "AWC per hour - DENSEST tCDS Hour", y = "AWC per hour - ALL DAY", title = "Spanish") + 
  annotate("text", x = 2000, y = 4000, label = "paste(r, \" = .79\")", parse = TRUE, size = 10) +
  theme(text = element_text(size = 25))
ggsave("./figures/corr_tophr_allday_sp.pdf", width = 10, height = 8) 

cor.test(tophr_allday_sp$awc_perhr_densest, tophr_allday_sp$awc_perhr_cleaned)

```
