---
title: "Descriptives of Duration of Activities"
author: "Janet Bang"
date: "November 17, 2022"
output:
  html_document: 
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This code is for the duration-based activity information. 


### Load libraries and set theme
```{r}
library(tidyverse)
library(gridExtra)
library(psych)

theme_set(theme_bw())
```


# Prep data
### Read in data and demographic information
```{r}
data_dur <- read_csv("./data_demo_lena_transcripts/elan_activity_dur.csv") %>% 
  mutate(id = factor(id), 
         language = factor(language)) %>% 
  dplyr::select(-X1) %>% 
  rename(tcds_min_seg = tcds_min) %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))

str(data_dur)


# create two dfs for plots
data_dur_en <- data_dur %>% filter(language == "english")
data_dur_sp <- data_dur %>% filter(language == "spanish")

```


### Check number of segments per participant
```{r}
# checking to see there are 6 segments per participant
num_segments_english <- data_dur_en %>% 
  group_by(id, segment_num) %>% 
  distinct(segment_num) %>% 
  ungroup() %>% 
  count(id)

arrange(num_segments_english, n)


num_segments_spanish <- data_dur_sp %>% 
  group_by(id, segment_num) %>% 
  distinct(segment_num) %>% 
  ungroup() %>% 
  count(id)

arrange(num_segments_spanish, n)

```



### Proportion duration - RAW per 10 min
```{r}
# duration - minutes
ggplot(data_dur, aes(activity, dur_min, fill = activity)) +
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) +
  theme(legend.position= "none") +
  # theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7), 
        text = element_text(size = 30)) + 
  labs(x = "Activity", y = "Duration (min)") + 
  theme(panel.spacing = unit(4, "lines"))
ggsave("./figures/boxplot_duration.pdf", dpi = 300, width = 18, height = 8, units = "in")


# summarize data per participant and activity (all speech only)
# english
data_en_act <- data_dur_en %>% 
  group_by(id, activity) %>% 
  mutate(dur_min_act = mean(dur_min)) %>% 
  distinct(id, language, activity, dur_min_act) %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))

# see min and max of actual data
data_dur_en %>% 
  ungroup() %>% 
  group_by(id, activity) %>% 
  mutate(min = min(dur_min), 
         max = max(dur_min)) %>% 
  distinct(activity, min, max)



# spanish
# note that min and max are of averages, not of actual data
data_sp_act <- data_dur_sp %>% 
  group_by(id, activity) %>% 
  mutate(dur_min_act = mean(dur_min)) %>% 
  distinct(id, language, activity, dur_min_act) %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))

# see min and max of actual data
data_dur_sp %>% 
  ungroup() %>% 
  group_by(activity) %>% 
  mutate(min = min(dur_min), 
         max = max(dur_min)) %>% 
  distinct(activity, min, max)



# descriptives
# note that min and max are of averages, not of actual data
describeBy(data_en_act$dur_min_act, data_en_act$activity, mat = T, fast = T)
describeBy(data_sp_act$dur_min_act, data_sp_act$activity, mat = T, fast = T)
```




### Proportion duration - summed across segments
```{r}
# duration - minutes
data_dur_sum <- data_dur %>% 
  group_by(id, activity) %>% 
  mutate(dur_act_total = sum(dur_min)) %>% 
  distinct(id, language, activity, dur_act_total) %>% 
  ungroup() %>% 
  group_by(id) %>% 
  mutate(dur_hour = sum(dur_act_total))

ggplot(data_dur_sum, aes(activity, dur_act_total, fill = activity)) +
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) +
  theme(legend.position= "none") +
  # theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7), 
        text = element_text(size = 30)) + 
  labs(x = "Activity", y = "Sum Duration Across Segments (min)") + 
  theme(panel.spacing = unit(4, "lines"))


data_dur_sum_en <- data_dur_sum %>% filter(language == "english")
data_dur_sum_sp <- data_dur_sum %>% filter(language == "spanish")


# descriptives
# note that min and max are of averages, not of actual data
describeBy(data_dur_sum_en$dur_act_total, data_dur_sum_en$activity, mat = T, fast = T)
describeBy(data_dur_sum_sp$dur_act_total, data_dur_sum_sp$activity, mat = T, fast = T)
```


### Proportion duration - other child-centered
```{r}
# duration - minutes
data_dur_othercc <- data_dur %>% 
  mutate(activity2 = ifelse(activity == "books", "books",
                     ifelse(activity == "ac", "ac",
                     ifelse(activity == "non-tcds", "non-tcds", "othercc")))) %>% 
  group_by(id, activity2) %>% 
  mutate(dur_act_total = sum(dur_min)) %>% 
  distinct(id, language, activity2, dur_act_total) %>% 
  ungroup() %>% 
  group_by(id) %>% 
  mutate(dur_hour = sum(dur_act_total))

data_dur_othercc_en <- data_dur_othercc %>% filter(language == "english")
data_dur_othercc_sp <- data_dur_othercc %>% filter(language == "spanish")


# descriptives
# note that min and max are of averages, not of actual data
describeBy(data_dur_othercc_en$dur_act_total, data_dur_othercc_en$activity2, mat = T, fast = T)
describeBy(data_dur_othercc_sp$dur_act_total, data_dur_othercc_sp$activity2, mat = T, fast = T)
```


# Plotting activity by time of day
## For publication
```{r, fig.height = 7, fig.width = 10}
data_dur_pub <- data_dur %>% 
  mutate(activity = recode(activity, "ac" = "Adult-cent.", "conv" = "Unst. Conv.", 
                           "books" = "Books", "play" = "Playing", "food" = "Feeding", 
                           "routines" = "Routines", "non-tcds" = "non-tCDS"), 
         language = recode(language, "english" = "English", "spanish" = "Spanish")) %>% 
  rename("Language" = "language") %>% 
  mutate(activity = factor(activity, levels = c("Books", "Playing", "Feeding", "Routines", "Unst. Conv.", "Adult-cent.", "non-tCDS")))

# combined groups
ggplot(data_dur_pub, aes(Time, fct_rev(activity), color = activity, shape = Language)) + 
  geom_jitter(size = 10, alpha = .5, stroke = 2) + 
  scale_x_continuous(breaks = c(5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24)) +
  scale_color_manual(values = c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "lightgrey"), guide = "none") + 
  scale_shape_manual(values=c(16, 21)) + 
  geom_vline(xintercept = 8) +
  geom_vline(xintercept = 12) + 
  geom_vline(xintercept = 16) +
  geom_vline(xintercept = 20) + 
  theme(text = element_text(size = 40)) +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1),
        legend.box.margin=margin(c(10,10,10,10)),
        legend.background = element_rect(fill = "white"), # , color = "black"
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 21), 
        legend.key.size = unit(1, "cm")) +
  labs(x = "Time", y = "")
  # theme(axis.title.y = element_text(angle = 0,  vjust = 0.5))

ggsave("./figures/time_activity_by_dur.pdf", width = 22, height = 11, dpi = 300)
```




# Pie charts for proportion duration of time per hour across families (adding time across six segments)
## Create dfs for individual participants
```{r}
# create duration per hour
total_dur_hour <- data_dur %>% 
  distinct(id, segment_num, rectime, Dur10minval, language) %>% 
  group_by(id) %>% 
  mutate(dur_six_segments = sum(Dur10minval)/60) %>% 
  distinct(id, dur_six_segments, language)


# merge with summary of dur per activity in one hour
variables_dur_all <- data_dur %>% 
  filter(activity != "non-tcds") %>% 
  dplyr::select(-c(dur_10min, tcds_min_seg)) %>% 
  full_join(total_dur_hour, by = c("id", "language")) %>% 
  group_by(id, activity) %>% 
  mutate(dur_activity_1hr = sum(dur_min)) %>% 
  distinct(id, activity, dur_activity_1hr, dur_six_segments, language)


# make wide, add zeros, make long, create proportion variable
data_dur_prop_all <- variables_dur_all %>% 
  spread(activity, dur_activity_1hr) %>% 
  replace_na(list(play = 0, food = 0, conv = 0, books = 0, routines = 0, ac = 0)) %>% 
  mutate(nontcds = dur_six_segments - (play + food + conv + books + routines + ac)) %>% 
  gather(activity, value = dur_activity_1hr_zeros, 
         play, food, conv, books, routines, ac, nontcds) %>% 
  mutate(prop_dur_activity_1hr = dur_activity_1hr_zeros / dur_six_segments) %>% 
  mutate(activity = factor(activity))


# create wide df for min per activity
data_dur_min_all_wide <- data_dur_prop_all %>% 
  dplyr::select(-prop_dur_activity_1hr) %>% 
  spread(activity, dur_activity_1hr_zeros) %>% 
  mutate(dur_min_total = ac + books + conv + food + nontcds + play + routines) %>% 
  mutate(dur_min_childcc = books + conv + food + play + routines) %>% 
  mutate(dur_min_tcds = ac + books + conv + food + play + routines)

psych::describeBy(data_dur_min_all_wide, data_dur_min_all_wide$language, fast = T)


# create wide df for prop min per activity
data_dur_prop_all_wide <- data_dur_prop_all %>% 
  dplyr::select(-dur_activity_1hr_zeros) %>% 
  spread(activity, prop_dur_activity_1hr) %>% 
  mutate(prop_total = ac + books + conv + food + nontcds + play + routines) %>% 
  mutate(prop_childcc = books + conv + food + play + routines) %>% 
  mutate(prop_tcds = ac + books + conv + food + play + routines)

# descriptives for proportion of min per activity
psych::describeBy(data_dur_prop_all_wide, data_dur_prop_all_wide$language, fast = T)
```



## Create dfs for single mean values across families
```{r}
prop_dur_mean_1hr_all <- data_dur_prop_all %>% 
  group_by(activity, language) %>% 
  dplyr::summarize(mean = mean(prop_dur_activity_1hr, na.rm=TRUE)) %>% 
  ungroup() %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))
  
prop_dur_mean_1hr_all %>% spread(activity, mean)
```



## For publication
```{r, fig.height = 7, fig.width = 10}
prop_dur_mean_1hr_all_pub <- prop_dur_mean_1hr_all %>% 
  mutate(language = recode(language, "english" = "English", "spanish" = "Spanish")) %>% 
  mutate(activity = recode(activity, "ac" = "adult-cent.", "conv" = "unst. conv.", "nontcds" = "non-tcds")) 

ggplot(prop_dur_mean_1hr_all_pub, aes(x="", y = mean, fill = activity)) + 
  theme_classic() +
  geom_bar(width = 1, stat = "identity") +
  coord_polar("y", start = 0) +
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "grey92")) + 
  geom_text(aes(label = paste0(round(mean*100), "%")), position = position_stack(vjust = 0.5), size = 20) + 
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank()) + 
  # scale_y_continuous(breaks = y.breaks,   # where to place the labels
  #                    labels = prop_dur_mean_1hr_all_pub$activity) + # the labels
  labs(title = "", x = "", y = "") +
  theme(text = element_text(size = 60),
        legend.position = "none") +
  # theme(legend.direction = "horizontal", 
        # legend.position = "bottom") +
  facet_wrap(~ language)
ggsave("./figures/piechart_dur_1hr.pdf", width = 24, height = 24, units = "in", dpi = 300)
```


# Additional figures (not in publication)
## Bar plot of each family and proportion duration per hour - sorted by AWC in one hour
```{r}
# total awc per hour
total_awc_hour <- data_dur %>% 
  distinct(id, segment_num, rectime, AWCval, language) %>% 
  group_by(id) %>% 
  mutate(awc_total_tophr = sum(AWCval)) %>% 
  distinct(id, awc_total_tophr, language)


data_dur_prop_en <- data_dur_prop_all %>% 
  full_join(total_awc_hour, by = c("id", "language")) %>% 
  filter(language == "english") %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "nontcds")))

data_dur_prop_sp <- data_dur_prop_all %>% 
  full_join(total_awc_hour, by = c("id", "language")) %>% 
  filter(language == "spanish") %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "nontcds")))


# plots
ggplot(data_dur_prop_en, aes(x = reorder(id, awc_total_tophr),  y = prop_dur_activity_1hr, fill = activity)) + 
  geom_col() + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "dodgerblue1", "green2", "darkgoldenrod1", "darkgrey", "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


ggplot(data_dur_prop_sp, aes(x = reorder(id, awc_total_tophr),  y = prop_dur_activity_1hr, fill = activity)) + 
  geom_col() + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "dodgerblue1", "green2", "darkgoldenrod1", "darkgrey", "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))



# plots - highlighting book reading
ggplot(data_dur_prop_en, aes(x = reorder(id, awc_total_tophr),  y = prop_dur_activity_1hr, fill = activity)) + 
  geom_col() + 
  scale_fill_manual(values=c("darkviolet", "grey", "grey", "grey", "grey", "grey", "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


ggplot(data_dur_prop_sp, aes(x = reorder(id, awc_total_tophr),  y = prop_dur_activity_1hr, fill = activity)) + 
  geom_col() + 
  scale_fill_manual(values=c("darkviolet", "grey", "grey", "grey", "grey", "grey", "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Instance of each activity per participant
```{r, fig.height = 7, fig.width = 14}
ggplot(data_dur_en, aes(id, fct_rev(activity), color = activity)) + 
  geom_point(size = 8) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "dodgerblue1", "green2", "darkgoldenrod1", "darkgrey", "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(data_dur_sp, aes(id, fct_rev(activity), color = activity)) + 
  geom_point(size = 8) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "dodgerblue1", "green2", "darkgoldenrod1", "darkgrey", "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

