---
title: "Descriptives of Duration of Activities"
author: "Janet Bang"
date: "April 25, 2025"
output:
  html_document: 
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This code is for the duration-based activity information and other supplemental figures. 


### Load libraries and set theme
```{r}
library(tidyverse)
library(gridExtra)
library(psych)

theme_set(theme_bw())
```


# Prep data
### Read in data and demographic information
```{r}
data_dur <- read_csv("./data_demo_lena_transcripts/elan_activity_dur.csv") %>% 
  mutate(id = factor(id), 
         language = factor(language)) %>% 
  dplyr::select(-"...1") %>% 
  rename(tcds_min_seg = tcds_min) %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))

str(data_dur)


# create two dfs for plots
data_dur_en <- data_dur %>% filter(language == "english")
data_dur_sp <- data_dur %>% filter(language == "spanish")

```


### Check number of segments per participant
```{r}
# checking to see there are 6 segments per participant
num_segments_english <- data_dur_en %>% 
  group_by(id, segment_num) %>% 
  distinct(segment_num) %>% 
  ungroup() %>% 
  count(id)

arrange(num_segments_english, n)


num_segments_spanish <- data_dur_sp %>% 
  group_by(id, segment_num) %>% 
  distinct(segment_num) %>% 
  ungroup() %>% 
  count(id)

arrange(num_segments_spanish, n)

```



### Proportion duration - RAW per 10 min
```{r}
# duration - minutes
ggplot(data_dur, aes(activity, dur_min, fill = activity)) +
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .2) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) +
  theme(legend.position= "none") +
  # theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7), 
        text = element_text(size = 30)) + 
  labs(x = "Activity", y = "Duration (min)") + 
  theme(panel.spacing = unit(4, "lines"))


# summarize data per participant and activity (all speech only)

# english
data_en_act <- data_dur_en %>% 
  group_by(id, activity) %>% 
  mutate(dur_min_act = mean(dur_min)) %>% 
  distinct(id, language, activity, dur_min_act) %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))

# see min and max of actual data
data_dur_en %>% 
  ungroup() %>% 
  group_by(id, activity) %>% 
  mutate(min = min(dur_min), 
         max = max(dur_min)) %>% 
  distinct(activity, min, max)



# spanish
# note that min and max are of averages, not of actual data
data_sp_act <- data_dur_sp %>% 
  group_by(id, activity) %>% 
  mutate(dur_min_act = mean(dur_min)) %>% 
  distinct(id, language, activity, dur_min_act) %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", "routines", "conv", "ac", "non-tcds")))

# see min and max of actual data
data_dur_sp %>% 
  ungroup() %>% 
  group_by(activity) %>% 
  mutate(min = min(dur_min), 
         max = max(dur_min)) %>% 
  distinct(activity, min, max)



# descriptives
# note that min and max are of averages, not of actual data
describeBy(data_en_act$dur_min_act, data_en_act$activity, mat = T, fast = T)
describeBy(data_sp_act$dur_min_act, data_sp_act$activity, mat = T, fast = T)
```




### Proportion duration - TOTAL SUM across segments (not including 0s)
```{r}
# duration - minutes
data_dur_sum <- data_dur %>% 
  group_by(id, activity) %>% 
  mutate(dur_act_total = sum(dur_min)) %>% 
  distinct(id, language, activity, dur_act_total) %>% 
  ungroup() %>% 
  group_by(id) %>% 
  mutate(dur_hour = sum(dur_act_total), 
         activity2 = ifelse(activity == "books", "Books", 
                     ifelse(activity == "play", "Playing", 
                     ifelse(activity == "food", "Feeding", 
                     ifelse(activity == "routines", "Routines", 
                     ifelse(activity == "conv", "Unst. Conv.", 
                     ifelse(activity == "ac", "Adult-cent.", "non-tCDS")))))), 
         activity2 = factor(activity2, levels = c("Books", "Playing", "Feeding", "Routines", 
                                                  "Unst. Conv.", "Adult-cent.", "non-tCDS")))

ggplot(data_dur_sum, aes(activity2, dur_act_total, fill = activity2)) +
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "lightgrey")) + 
  facet_wrap(~ language) +
  theme(legend.position= "none") +
  # theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7), 
        text = element_text(size = 30)) + 
  labs(x = "Activity", y = "Sum Duration Across Segments (min)") + 
  theme(panel.spacing = unit(4, "lines"))


data_dur_sum_en <- data_dur_sum %>% filter(language == "english")
data_dur_sum_sp <- data_dur_sum %>% filter(language == "spanish")


# descriptives
# note that min and max are of averages, not of actual data
describeBy(data_dur_sum_en$dur_act_total, data_dur_sum_en$activity, mat = T, fast = T)
describeBy(data_dur_sum_sp$dur_act_total, data_dur_sum_sp$activity, mat = T, fast = T)
```



### Proportion duration - other-child-centered
```{r}
# duration - minutes
data_dur_othercc <- data_dur %>% 
  mutate(activity2 = ifelse(activity == "books", "books",
                     ifelse(activity == "ac", "ac",
                     ifelse(activity == "non-tcds", "non-tcds", "othercc")))) %>% 
  group_by(id, activity2) %>% 
  mutate(dur_act_total = sum(dur_min)) %>% 
  distinct(id, language, activity2, dur_act_total) %>% 
  ungroup() %>% 
  group_by(id) %>% 
  mutate(dur_hour = sum(dur_act_total))

data_dur_othercc_en <- data_dur_othercc %>% filter(language == "english")
data_dur_othercc_sp <- data_dur_othercc %>% filter(language == "spanish")


# descriptives
# note that min and max are of averages, not of actual data
describeBy(data_dur_othercc_en$dur_act_total, data_dur_othercc_en$activity2, mat = T, fast = T)
describeBy(data_dur_othercc_sp$dur_act_total, data_dur_othercc_sp$activity2, mat = T, fast = T)
```



# Plotting activity by time of day
## For publication
```{r, fig.height = 7, fig.width = 10}
data_dur_pub <- data_dur %>% 
  mutate(activity = recode(activity, "ac" = "Adult-cent.", "conv" = "Unst. Conv.", 
                           "books" = "Books", "play" = "Playing", "food" = "Feeding", 
                           "routines" = "Routines", "non-tcds" = "non-tCDS"), 
         language = recode(language, "english" = "English", "spanish" = "Spanish")) %>% 
  rename("Language" = "language") %>% 
  mutate(activity = factor(activity, levels = c("Books", "Playing", "Feeding", "Routines", "Unst. Conv.", "Adult-cent.", "non-tCDS")))

# combined groups
ggplot(data_dur_pub, aes(Time, fct_rev(activity), color = activity, shape = Language)) + 
  geom_jitter(size = 10, alpha = .5, stroke = 2) + 
  scale_x_continuous(breaks = c(5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24)) +
  scale_color_manual(values = c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "lightgrey"), guide = "none") + 
  scale_shape_manual(values=c(16, 21)) + 
  geom_vline(xintercept = 8) +
  geom_vline(xintercept = 12) + 
  geom_vline(xintercept = 16) +
  geom_vline(xintercept = 20) + 
  theme(text = element_text(size = 40)) +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1),
        legend.box.margin=margin(c(10,10,10,10)),
        legend.background = element_rect(fill = "white"), # , color = "black"
        legend.text = element_text(size = 18), 
        legend.title = element_text(size = 21), 
        legend.key.size = unit(1, "cm")) +
  labs(x = "Time", y = "")
  # theme(axis.title.y = element_text(angle = 0,  vjust = 0.5))

ggsave("./figures/time_activity_by_dur.pdf", width = 22, height = 11, dpi = 300)
```


## Examining continguity of segments (supplemental analyses)
```{r}
ggplot(data_dur, aes(Time, id, color = language)) + 
  geom_point(size = 3) + 
  theme(axis.text.y = element_blank()) + 
  geom_vline(xintercept = 6, color = "darkgrey") + 
  geom_vline(xintercept = 7, color = "darkgrey") +   
  geom_vline(xintercept = 8, color = "darkgrey") +   
  geom_vline(xintercept = 9, color = "darkgrey") +   
  geom_vline(xintercept = 10, color = "darkgrey") +        
  geom_vline(xintercept = 11, color = "darkgrey") +   
  geom_vline(xintercept = 12, color = "darkgrey") +
  geom_vline(xintercept = 13, color = "darkgrey") +
  geom_vline(xintercept = 14, color = "darkgrey") +
  geom_vline(xintercept = 15, color = "darkgrey") +
  geom_vline(xintercept = 16, color = "darkgrey") +
  geom_vline(xintercept = 17, color = "darkgrey") +
  geom_vline(xintercept = 18, color = "darkgrey") +
  geom_vline(xintercept = 19, color = "darkgrey") +
  geom_vline(xintercept = 20, color = "darkgrey") +
  geom_vline(xintercept = 21, color = "darkgrey") +
  geom_vline(xintercept = 22, color = "darkgrey") +
  geom_vline(xintercept = 23, color = "darkgrey") +
  geom_vline(xintercept = 24, color = "darkgrey")
  labs(x = "Time", y = "Participant")
  

ggsave("./figures/sampling_byTime_perID.pdf", width = 11, height = 8.5, dpi = 300)

```



## Examining the number of activities per segment
```{r}
# calculate number of activities per segment
data_dur3 <- data_dur %>% 
  ungroup() %>% 
  filter(activity != "non-tcds") %>% 
  dplyr::select(c(id, activity, segment_num, language)) %>% 
  group_by(id, segment_num, language) %>% 
  count()

psych::describe(data_dur3$n, fast = T)

psych::describeBy(data_dur3$n, data_dur3$language, fast = T)
```



# Proportion duration of time per hour across families (adding time across six segments, including 0s) - For publication
## Create dfs for individual participants
```{r}
# create duration per hour
total_dur_hour <- data_dur %>% 
  distinct(id, segment_num, rectime, Dur10minval, language) %>% 
  group_by(id) %>% 
  mutate(dur_six_segments = sum(Dur10minval)/60) %>% 
  distinct(id, dur_six_segments, language)

# data_dur_sum <- data_dur %>% 
#   group_by(id, activity) %>% 
#   mutate(dur_act_total = sum(dur_min)) %>% 
#   distinct(id, language, activity, dur_act_total) %>% 
#   ungroup() %>% 
#   group_by(id) %>% 
#   mutate(dur_hour = sum(dur_act_total))


# merge with summary of dur per activity in one hour
variables_dur_all <- data_dur %>% 
  filter(activity != "non-tcds") %>% 
  dplyr::select(-c(dur_10min, tcds_min_seg)) %>% 
  full_join(total_dur_hour, by = c("id", "language")) %>% 
  group_by(id, activity) %>% 
  mutate(dur_activity_1hr = sum(dur_min)) %>% 
  distinct(id, activity, dur_activity_1hr, dur_six_segments, language)


# make wide, add zeros, make long, create proportion variable
data_dur_prop_all <- variables_dur_all %>% 
  spread(activity, dur_activity_1hr) %>% 
  replace_na(list(play = 0, food = 0, conv = 0, books = 0, routines = 0, ac = 0)) %>% 
  mutate(nontcds = dur_six_segments - (play + food + conv + books + routines + ac)) %>% 
  gather(activity, value = dur_activity_1hr_zeros, 
         play, food, conv, books, routines, ac, nontcds) %>% 
  mutate(prop_dur_activity_1hr = dur_activity_1hr_zeros / dur_six_segments) %>% 
  mutate(activity = factor(activity))


# create wide df for min per activity
data_dur_min_all_wide <- data_dur_prop_all %>% 
  dplyr::select(-prop_dur_activity_1hr) %>% 
  spread(activity, dur_activity_1hr_zeros) %>% 
  mutate(dur_min_total = ac + books + conv + food + nontcds + play + routines) %>% 
  mutate(dur_min_childcc = books + conv + food + play + routines) %>% 
  mutate(dur_min_tcds = ac + books + conv + food + play + routines)

psych::describeBy(data_dur_min_all_wide, data_dur_min_all_wide$language, fast = T)


# create wide df for prop min per activity
data_dur_prop_all_wide <- data_dur_prop_all %>% 
  dplyr::select(-dur_activity_1hr_zeros) %>% 
  spread(activity, prop_dur_activity_1hr) %>% 
  mutate(prop_total = ac + books + conv + food + nontcds + play + routines) %>% 
  mutate(prop_childcc = books + conv + food + play + routines) %>% 
  mutate(prop_tcds = ac + books + conv + food + play + routines)

# descriptives for proportion of min per activity
psych::describeBy(data_dur_prop_all_wide, data_dur_prop_all_wide$language, fast = T)
```



## For publication - boxplot
```{r}
# make proportions long again
data_dur_prop_all_forpub <- data_dur_prop_all_wide %>% 
  dplyr::select(id, language, ac, books, conv, food, nontcds, play, routines, prop_total, prop_childcc, prop_tcds) %>% 
  rename(Books = books, "Unst. Conv." = conv, Feeding = food, 
         "non-tCDS" = nontcds, Playing = play, Routines = routines, 
         "Only Child-cent." = prop_childcc, 
         "All tCDS" = prop_tcds, "Adult-cent." = ac) %>% 
  mutate(language2 = ifelse(language == "english", "English", "Spanish")) %>% 
  pivot_longer(cols = "Adult-cent.": "All tCDS", 
               names_to = "activity", 
               values_to = "proportion") %>% 
  mutate(activity = factor(activity, levels = c("Books", "Playing", "Feeding", 
                                                "Routines", "Unst. Conv.", "Adult-cent.", 
                                                "non-tCDS", "Only Child-cent.", "All tCDS"))) %>% 
  filter(activity != "Only Child-cent." & activity != "All tCDS")


# boxplot
ggplot(data_dur_prop_all_forpub, aes(activity, proportion, fill = activity)) +
  theme_classic() +
  geom_boxplot(alpha = .8, outlier.shape = NA) + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "lightgrey")) + 
  stat_summary(fun ="mean", size = 2, shape = 18) + 
  facet_wrap(~ language2) +
  labs(x = "Activity", y = "Proportion \nDuration \n(out of 1 hour)") + 
  theme(legend.position= "none",
        axis.text.x = element_text(angle = 30, hjust = .7), 
        text = element_text(size = 25), 
        axis.title.y = element_text(angle = 0, vjust = 0.5), 
        panel.spacing = unit(4, "lines"))

ggsave("./figures/boxplot_dur_1hr_w_mean.pdf", width = 19, height = 9, units = "in", dpi = 300)

```

