---
title: "Descriptives of Caregiver Speech - Transcription data"
author: "Janet Bang"
date: "November 17, 2022"
output:
  html_document: 
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r, echo = F}
library(knitr)
opts_chunk$set(echo=TRUE, 
               warning=FALSE, message=FALSE, 
               cache=FALSE)
options(width = 100)

opts_chunk$set(fig.width = 12, fig.height = 12) 
```


This code is for the caregiver speech measures from transcripts used in the manuscript. 


### Load libraries and set theme
```{r}
library(tidyverse)
library(Hmisc)
library(GGally)
library(ppcor)
library(gridExtra)
library(psych)

# https://github.com/ggobi/ggally/issues/139
my_custom_smooth <- function(data, mapping, ...) {
  ggplot(data = data, mapping = mapping) +
    geom_point(alpha = .4, color = I("black")) + 
    geom_smooth(method = "lm", color = I("blue"), ...)
}

theme_set(theme_bw())
```


## Read in data
```{r}
# NOTE about periods of non-tCDCS
# gemods refers to when there are designated start/end periods of other-directed speech (ODS); this was captured using gems (@G) using CHAT conventions
# kwalods refers to when ODS was transcribed at an utterance-level within a tCDS activity period between caregiver and child (e.g., other-directed speech in the background); this was captured per utterances using CHAT postcodes
## for tokens/min and types/min, we do not include ODS that occurred within a period of tCDS, because durations were captured by activity and not by utterance
## for mlu, we include all ODS across gemods and kwalods


# NOTE about speech == "all"
# "speech" includes two levels: all, spont
# all = refers to all speech by caregivers
# spont = refers to only speech by caregivers that was considered spontaneous rather than recited (e.g., reading book text, singing memorized common songs like itsy bitsy spider); therefore, 'spont' is a subset of 'all'

# freq
freq <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  dplyr::select(-X1) %>% 
  filter(activity != "kwalods") %>% 
  filter(speech == "all") %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", 
                                                "routines", "conv", "ac", 
                                                "gemods")), 
         id = factor(id), 
         language = factor(language), 
         speech = factor(speech))


# mlu
mlu <- read_csv("./data_demo_lena_transcripts/mlu.csv") %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", 
                                                "routines", "conv", "ac", "ods")), 
         id = factor(id), 
         language = factor(language), 
         speech = factor(speech)) %>% 
  filter(speech == "all")


# chip
# this includes only caregivers, therefore there is no speaker column
# we exclude periods of ODS because this is about responsiveness to the child during periods of tCDS
chip <- read_csv("./data_demo_lena_transcripts/chip.csv") %>% 
  filter(activity != "ods") %>% 
  mutate(activity = factor(activity, levels = c("books", "play", "food", 
                                                "routines", "conv", "ac")), 
         id = factor(id), 
         language = factor(language)) 

str(freq)
str(mlu)
str(chip)
```



## Create dfs for ADULTS
```{r}
# FREQ
freq_adult <- freq %>% 
  filter(speaker == "ADULTS")

# MLU
mlu_adult <- mlu %>% 
  filter(speaker == "ADULTS")

```




# FREQ - Boxplots and descriptives for ADULTS
## TOKENS (raw)


Freq (tokens, types)

* excluded non-target children (NTC)
* excluded overlapping ODS during CDS periods
* averaged across all adult speakers
* if an activity was not present, we did not include it (i.e., we did not impute any values to create complete cases)
* 0 values are included when the individual does not speak though we know they are present in the activity


```{r}
# relabel for plots
freq_adult <- freq_adult %>% 
  mutate(activity = recode(activity, "conv" = "unst. conv.", "ac" = "adult-centered",
                                     "gemods" = "non_tcds"), 
         language = recode(language, "English" = "english", "Spanish" = "spanish"))


# plot for all speech
ggplot(freq_adult, aes(activity, tokens, fill = activity)) + 
  geom_boxplot() + 
  geom_jitter(alpha = .2) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language, ncol = 1) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "")


# summarize data per participant and activity (all speech only)
freq_adult_act <- freq_adult %>% 
  group_by(id, activity) %>% 
  mutate(tokens_act = mean(tokens), 
         types_act = mean(types)) %>% 
  distinct(id, language, activity, tokens_act, types_act)

freq_adult_act_en <- freq_adult_act %>% filter(language == "english")
freq_adult_act_sp <- freq_adult_act %>% filter(language == "spanish")



# descriptives
describeBy(freq_adult_act_en$tokens_act, freq_adult_act_en$activity, mat = T, fast = T)

freq_adult_en_minmax_tokens_raw <- freq_adult %>% 
  filter(language == "english") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(tokens, na.rm = T), 
         max = max(tokens, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_en_minmax_tokens_raw

describeBy(freq_adult_act_sp$tokens_act, freq_adult_act_sp$activity, mat = T, fast = T)

freq_adult_sp_minmax_tokens_raw <- freq_adult %>% 
  filter(language == "spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(tokens, na.rm = T), 
         max = max(tokens, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_sp_minmax_tokens_raw

```



## TOKENS (rate per min)
```{r}
freq_adult <- freq_adult %>% 
  mutate(language = recode(language, "english" = "English", "spanish" = "Spanish"))


# plot for all speech
ggplot(freq_adult, aes(activity, tokens_permin, fill = activity)) + 
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "Tokens Rate") + 
  theme(panel.spacing = unit(4, "lines"))
ggsave("./figures/boxplot_tokens_rate2.pdf", dpi = 300, width = 18, height = 8, units = "in")


# summarize data per participant and activity (all speech only)
freq_adult_act_permin <- freq_adult %>% 
  group_by(id, activity) %>% 
  mutate(tokens_permin_act = mean(tokens_permin), 
         types_permin_act = mean(types_permin)) %>% 
  distinct(id, language, activity, tokens_permin_act, types_permin_act)

freq_adult_act_permin_en <- freq_adult_act_permin %>% filter(language == "English")
freq_adult_act_permin_sp <- freq_adult_act_permin %>% filter(language == "Spanish")

# descriptives
describeBy(freq_adult_act_permin_en$tokens_permin_act, freq_adult_act_permin_en$activity, mat = T, fast = T)

freq_adult_en_minmax_tokens_rate <- freq_adult %>% 
  filter(language == "English") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(tokens_permin, na.rm = T), 
         max = max(tokens_permin, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_en_minmax_tokens_rate

describeBy(freq_adult_act_permin_sp$tokens_permin_act, freq_adult_act_permin_sp$activity, mat = T, fast = T)

freq_adult_sp_minmax_tokens_rate <- freq_adult %>% 
  filter(language == "Spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(tokens_permin, na.rm = T), 
         max = max(tokens_permin, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_sp_minmax_tokens_rate
```



## TYPES (raw)
```{r}
# df for just all speech
ggplot(freq_adult, aes(activity, types, fill = activity)) +
  geom_boxplot() + 
  geom_jitter(alpha = .2) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "")


# descriptives
describeBy(freq_adult_act_en$types_act, freq_adult_act_en$activity, mat = T, fast = T)

freq_adult_en_minmax_types_raw <- freq_adult %>% 
  filter(language == "English") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(types, na.rm = T), 
         max = max(types, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_en_minmax_types_raw



describeBy(freq_adult_act_sp$types_act, freq_adult_act_sp$activity, mat = T, fast = T)

freq_adult_sp_minmax_types_raw <- freq_adult %>% 
  filter(language == "Spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(types, na.rm = T), 
         max = max(types, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_sp_minmax_types_raw

```



## TYPES (rate per min)
```{r}
# plot for all speech
ggplot(freq_adult, aes(activity, types_permin, fill = activity)) + 
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "Types Rate")
ggsave("./figures/boxplot_types_rate2.pdf", dpi = 300, width = 18, height = 8, units = "in")


# descriptives
describeBy(freq_adult_act_permin_en$types_permin_act, freq_adult_act_permin_en$activity, mat = T, fast = T)

freq_adult_en_minmax_types_rate <- freq_adult %>% 
  filter(language == "English") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(types_permin, na.rm = T), 
         max = max(types_permin, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_en_minmax_types_rate


describeBy(freq_adult_act_permin_sp$types_permin_act, freq_adult_act_permin_sp$activity, mat = T, fast = T)

freq_adult_sp_minmax_types_rate <- freq_adult %>% 
  filter(language == "spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(types_permin, na.rm = T), 
         max = max(types_permin, na.rm = T)) %>% 
  distinct(activity, min, max)

freq_adult_sp_minmax_types_rate
```


# MLU

MLU

* excluded NTC 
* KEPT overlapping ODS during CDS periods
* averaged across all adult speakers
* if an activity was not present, we did not include it (i.e., we did not impute any values to create complete cases)
* we excluded observations when there were 0 number of utterances, since we cannot calculate an MLU when there are no utterances


```{r}
# relabel for plots
mlu_adult <- mlu_adult %>% 
  mutate(activity = recode(activity, "conv" = "unst. conv.", "ac" = "adult-centered",
                           "ods" = "non_tcds"), 
         language = recode(language, "english" = "English", "spanish" = "Spanish"))


# plot
ggplot(mlu_adult, aes(activity, mlu_w, fill = activity)) + 
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  facet_wrap(~ language) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "MLUw")
ggsave("./figures/boxplot_mluw2.pdf", dpi = 300, width = 18, height = 8, units = "in")


# summarize data per participant and activity (all speech only)
mlu_adult_act <- mlu_adult %>% 
  group_by(id, activity) %>% 
  mutate(mlu_w_act = mean(mlu_w)) %>% 
  distinct(id, language, activity, mlu_w_act)

mlu_adult_act_en <- mlu_adult_act %>% filter(language == "English")
mlu_adult_act_sp <- mlu_adult_act %>% filter(language == "Spanish")

# descriptives
describeBy(mlu_adult_act_en$mlu_w_act, mlu_adult_act_en$activity, mat = T, fast = T)

mlu_adult_en_minmax <- mlu_adult %>% 
  filter(language == "English") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(mlu_w, na.rm = T), 
         max = max(mlu_w, na.rm = T)) %>% 
  distinct(activity, min, max)

mlu_adult_en_minmax


describeBy(mlu_adult_act_sp$mlu_w_act, mlu_adult_act_sp$activity, mat = T, fast = T)

mlu_adult_sp_minmax <- mlu_adult %>% 
  filter(language == "Spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(mlu_w, na.rm = T), 
         max = max(mlu_w, na.rm = T)) %>% 
  distinct(activity, min, max)

mlu_adult_sp_minmax

```




# CHIP
## Responses (RAW and PROP)

CHIP (responses, imitations/expansions; these are utterances that follow a child's utterance, within a 5 utterance window)

* excluded NTC 
* excluded overlapping ODS during CDS periods
* averaged across all adult speakers
* if an activity was not present, we did not include it (i.e., we did not impute any values to create complete cases)
* we keep 0 values, which are because the adults did not respond even though the child did have utterances [e.g., numerator is 0 but denominator is a value]; if a child did not have utterances, then adult responses could not be calculated so the number of observations differ here from freq and mlu
* greater than 1 = caregiver had more utterances in response to the child; less than 1 = child had more utterances than caregiver responses


```{r}
# create dfs
chip2 <- chip %>% 
  mutate(activity = recode(activity, "conv" = "unst. conv.", "ac" = "adult-centered"), 
         language = recode(language, "english" = "English", "spanish" = "Spanish"))


# plot - total adult responses
ggplot(chip2, aes(activity, total_adult_resp, fill = activity)) + 
  geom_boxplot() + 
  geom_jitter(alpha = .2) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  facet_wrap(~ language, ncol = 1) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "")



# plot - prop of adult resp/child utt
ggplot(chip2, aes(activity, prop_adultresp_outof_childutt, fill = activity)) + 
  theme_classic() +
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  facet_wrap(~ language) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  geom_hline(yintercept = 1) + # caregiver and child = equal utts
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "Prop Responses")
ggsave("./figures/boxplot_prop_resp2.pdf", dpi = 300, width = 18, height = 8, units = "in")


# summarize data per participant and activity (all speech only)
chip_act <- chip %>% 
  group_by(id, activity) %>% 
  mutate(prop_resp_act = mean(prop_adultresp_outof_childutt), 
         prop_imitexp_act = mean(prop_adult_imitexp_outof_childutt)) %>% 
  distinct(id, language, activity, prop_resp_act, prop_imitexp_act)

chip_act_en <- chip_act %>% filter(language == "english")
chip_act_sp <- chip_act %>% filter(language == "spanish")


# descriptives
describeBy(chip_act_en$prop_resp_act, chip_act_en$activity, mat = T, fast = T)

chip_adult_en_minmax_propresp <- chip %>% 
  filter(language == "english") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(prop_adultresp_outof_childutt, na.rm = T), 
         max = max(prop_adultresp_outof_childutt, na.rm = T)) %>% 
  distinct(activity, min, max)

chip_adult_en_minmax_propresp

describeBy(chip_act_sp$prop_resp_act, chip_act_sp$activity, mat = T, fast = T)

chip_adult_sp_minmax_propresp <- chip %>% 
  filter(language == "spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(prop_adultresp_outof_childutt, na.rm = T), 
         max = max(prop_adultresp_outof_childutt, na.rm = T)) %>% 
  distinct(activity, min, max)

chip_adult_sp_minmax_propresp
```



## Imitations/Expansions (RAW and PROP)
```{r}
# plot
ggplot(chip2, aes(activity, total_adult_imitexp, fill = activity)) + 
  geom_boxplot() + 
  geom_jitter(alpha = .2) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  facet_wrap(~ language, ncol = 1) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "")



# plot
ggplot(chip2, aes(activity, prop_adult_imitexp_outof_childutt, fill = activity)) + 
  theme_classic() + 
  geom_boxplot() + 
  geom_jitter(alpha = .3) + 
  scale_fill_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  facet_wrap(~ language) + 
  theme(legend.position= "none") +
  theme(text = element_text(size = 35)) +
  geom_hline(yintercept = 1) + # caregiver and child = equal utts
  theme(axis.text.x = element_text(angle = 20, hjust = .7)) + 
  labs(x = "", y = "Prop Imitations/Expansions")
ggsave("./figures/boxplot_prop_imitexp2.pdf", dpi = 300, width = 18, height = 8, units = "in")


# descriptives
describeBy(chip_act_en$prop_imitexp_act, chip_act_en$activity, mat = T, fast = T)

chip_adult_en_minmax_propimitexp <- chip %>% 
  filter(language == "english") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(prop_adult_imitexp_outof_childutt, na.rm = T), 
         max = max(prop_adult_imitexp_outof_childutt, na.rm = T)) %>% 
  distinct(activity, min, max)

chip_adult_en_minmax_propimitexp

describeBy(chip_act_sp$prop_imitexp_act, chip_act_sp$activity, mat = T, fast = T)

chip_adult_sp_minmax_propimitexp <- chip %>% 
  filter(language == "spanish") %>% 
  group_by(activity, language) %>% 
  mutate(min = min(prop_adult_imitexp_outof_childutt, na.rm = T), 
         max = max(prop_adult_imitexp_outof_childutt, na.rm = T)) %>% 
  distinct(activity, min, max)

chip_adult_sp_minmax_propimitexp
```