---
title: "Caregiver Speech Mixed Models - 4 categories"
author: "Janet Bang"
date: "May 5, 2025"
output:
  html_document: 
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r, echo = F}
library(knitr)
opts_chunk$set(echo=TRUE, 
               warning=FALSE, message=FALSE, 
               cache=FALSE)
options(width = 100)

opts_chunk$set(fig.width = 12, fig.height = 8) 
```


This code is for the results to the question: Do features of caregiver verbal engagement vary as a function of language group and activity?


### Load libraries and set theme
```{r}
library(tidyverse)
library(ggpubr)
library(psych)
library(lme4)
library(lmerTest)
library(emmeans)
library(sjPlot)
library(ggeffects)

theme_set(theme_bw())

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}
```


# Read in data and convert
```{r}
# demographics
demo_english <- read_csv("./data_demo_lena_transcripts/demo_english_ms.csv") %>% 
  rename(id = ID, hi = HI24Final, momed = Momed) %>% 
  dplyr::select(id, hi, momed) %>% 
  mutate(id = as.character(id), 
         language = "english")

demo_spanish <- read_csv("./data_demo_lena_transcripts/demo_spanish_ms.csv") %>% 
  rename(id = ID, hi = HI_18, momed = MomEd_25m) %>% 
  dplyr::select(id, hi, momed) %>% 
  mutate(id = as.character(id), 
         language = "spanish")

demo <- rbind(demo_english, demo_spanish)



# NOTE about periods of non-tCDCS
# gemods refers to when there are designated start/end periods of other-directed speech (ODS); this was captured using gems (@G) using CHAT conventions
# kwalods refers to when ODS was transcribed at an utterance-level within a tCDS activity period between caregiver and child (e.g., other-directed speech in the background); this was captured per utterances using CHAT postcodes
## for tokens/min and types/min, we do not include ODS that occurred within a period of tCDS, because durations were captured by activity and not by utterance
## for mlu, we include all ODS across gemods and kwalods


# NOTE about speech == "all"
# "speech" includes two levels: all, spont
# all = refers to all speech by caregivers
# spont = refers to only speech by caregivers that was considered spontaneous rather than recited (e.g., reading book text, singing memorized common songs like itsy bitsy spider); therefore, 'spont' is a subset of 'all'


# freq
freq <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  filter(activity != "kwalods", 
         speech == "all") %>% 
  mutate(activity = recode(activity, "play" = "cc", "conv" = "cc", 
                           "food" = "cc", "routines" = "cc", "gemods" = "non_tcds")) %>% # we collapsed across play, routines, feeding, and unstructured conversation for the final paper [see supplemental for all categories]
  group_by(id, activity, segment_num, speaker) %>% 
  mutate(dur_min2 = sum(dur_min),
         tokens2 = sum(tokens), 
         types2 = mean(types)) %>% 
  distinct(id, activity, language, speaker, segment_num, tokens2, types2, dur_min2) %>% 
  mutate(tokens_permin2 = tokens2/dur_min2, 
         types_permin2 = types2/dur_min2) %>% 
  distinct(id, activity, language, speaker, segment_num, tokens_permin2, types_permin2) %>% 
  ungroup() %>% 
  mutate(activity = factor(activity, levels = c("books", "cc", "ac", "non_tcds")), 
         id = factor(id), 
         language = factor(language)) 


# mlu
mlu <- read_csv("./data_demo_lena_transcripts/mlu.csv") %>% 
  filter(speech == "all") %>% 
  mutate(activity = recode(activity, "play" = "cc", "conv" = "cc", 
                           "food" = "cc", "routines" = "cc", "ods" = "non_tcds")) %>% 
  group_by(id, activity, segment_num, speaker) %>% 
  mutate(words_sum2 = sum(words_sum),
         num_utt_sum2 = sum(num_utt_sum)) %>% 
  distinct(id, activity, language, speaker, segment_num, words_sum2, num_utt_sum2) %>% 
  group_by(id, activity, segment_num, speaker) %>% 
  mutate(mlu_w2 = words_sum2/num_utt_sum2) %>% 
  distinct(id, activity, language, speaker, segment_num, mlu_w2) %>% 
  ungroup() %>% 
  mutate(activity = factor(activity, levels = c("books", "cc", "ac", "non_tcds")), 
         id = factor(id), 
         language = factor(language))


# chip
# this includes only caregivers, therefore there is no speaker column
# we exclude periods of ODS because this is about responsiveness to the child during periods of tCDS
chip <- read_csv("./data_demo_lena_transcripts/chip.csv") %>% 
  filter(activity != "ods") %>% 
  mutate(activity = recode(activity, "play" = "cc", "conv" = "cc", 
                           "food" = "cc", "routines" = "cc")) %>% 
  group_by(id, activity, segment_num) %>% 
  mutate(total_adult_resp2 = sum(total_adult_resp),
         total_adult_imitexp2 = sum(total_adult_imitexp), 
         total_child_utt2 = sum(total_child_utt)) %>% 
  distinct(id, activity, language, segment_num, total_adult_resp2, total_adult_imitexp2, total_child_utt2) %>%
  mutate(prop_adultresp2 = total_adult_resp2/total_child_utt2, 
         prop_adult_imitexp2 = total_adult_imitexp2/total_child_utt2) %>% 
  distinct(id, activity, segment_num, language, prop_adultresp2, prop_adult_imitexp2) %>% 
  ungroup() %>% 
  mutate(activity = factor(activity, levels = c("books", "cc", "ac")), 
         id = factor(id), 
         language = factor(language))
  

str(freq)
str(mlu)
str(chip)
```




## Create dfs for ADULTS and CHI
```{r}
# FREQ
freq_adult <- freq %>% 
  filter(speaker == "ADULTS")


# MLU
mlu_adult <- mlu %>% 
  filter(speaker == "ADULTS")
```



# Prep data for mixed models
## Create tokens rate per hour - Children
```{r}
freq_hr_child <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  dplyr::select(-"...1") %>% 
  filter(speech == "all", 
         speaker == "CHI") %>% 
  group_by(id) %>% 
  mutate(tokens_sum_child = sum(tokens), 
         dur_hr = sum(dur_min)/60, 
         tokens_hr_child = tokens_sum_child/dur_hr) %>% 
  distinct(id, language, tokens_hr_child) %>% 
  ungroup() %>% 
  mutate(id = as.character(id))
```




## Merge freq_adult, child tokens per hour, and demographic info
```{r}
# freq
freq_all_mm <- freq_adult %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child, by = c("id", "language")) %>% 
  left_join(demo, by = c("id", "language")) %>% 
  mutate(id = as.factor(id), 
         language = as.factor(language), 
         segment_num = as.factor(segment_num))


# mlu
mlu_all_mm <- mlu_adult %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child, by = c("id", "language")) %>% 
  left_join(demo, by = c("id", "language")) %>% 
  mutate(id = as.factor(id), 
         language = as.factor(language), 
         segment_num = as.factor(segment_num))



# chip
chip_mm <- chip %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child, by = c("id", "language")) %>% 
  left_join(demo, by = c("id", "language")) %>% 
  mutate(id = as.factor(id), 
         language = as.factor(language), 
         segment_num = as.factor(segment_num))


```



# Mixed models - 4 categories - Language as Moderator
## TOKENS x ACTIVITY - BOTH - ALL TALK - LG as Moderator
```{r}
# comparing models
m1_both_tokens_all <- lmer(tokens_permin2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m2_both_tokens_all <- lmer(tokens_permin2 ~ tokens_hr_child + language + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m3_both_tokens_all <- lmer(tokens_permin2 ~ tokens_hr_child + (language * activity) +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

# see if adding the intx adds
anova(m1_both_tokens_all, m2_both_tokens_all, m3_both_tokens_all)

# anova table for final model
anova(m3_both_tokens_all)


# emmeans
# interaction - post hoc tests of simple effects
m3_both_tokens_all_emmeans_simple1 <- emmeans(m3_both_tokens_all, ~ activity | language)
m3_both_tokens_all_emmeans_simple2 <- emmeans(m3_both_tokens_all, ~ language | activity)

m3_both_tokens_all_emmeans_simple1


rbind(pairs(m3_both_tokens_all_emmeans_simple1), pairs(m3_both_tokens_all_emmeans_simple2))
confint(rbind(pairs(m3_both_tokens_all_emmeans_simple1), pairs(m3_both_tokens_all_emmeans_simple2)))



# plot
tokens_emmeans <- data.frame(emmeans(m3_both_tokens_all, ~ activity | language))


tokens <- ggplot(tokens_emmeans, aes(activity, emmean, colour = activity, shape = language, group = language)) + 
  geom_line(aes(group = language)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_shape_manual(values = c(16, 21), 
                     name="Language",
                     labels=c('English', 'Spanish')) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "grey", "black"),
                     name="Activity",
                     labels=c('Books','Other Child-Cent','Adult-Cent', 'non-tCDS')) +
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Other Child-Cent','Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "Tokens (rate per min)")

tokens
ggsave("./figures/emmeans_tokens_may5_2025.pdf", width = 6, height = 6, units = "in")

```




## TYPES x ACTIVITY - BOTH - ALL TALK - LG as Moderator
```{r}
m1_both_types_all <- lmer(types_permin2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m2_both_types_all <- lmer(types_permin2 ~ tokens_hr_child + language + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m3_both_types_all <- lmer(types_permin2 ~ tokens_hr_child + (language * activity) +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

# see if adding the intx adds
anova(m1_both_types_all, m2_both_types_all, m3_both_types_all)

# anova table for final model
anova(m3_both_types_all)



# emmeans
# interaction - post hoc tests of simple effects
m3_both_types_all_emmeans_simple1 <- emmeans(m3_both_types_all, ~ activity | language)
m3_both_types_all_emmeans_simple2 <- emmeans(m3_both_types_all, ~ language | activity)

m3_both_types_all_emmeans_simple1


rbind(pairs(m3_both_types_all_emmeans_simple1), pairs(m3_both_types_all_emmeans_simple2))
confint(rbind(pairs(m3_both_types_all_emmeans_simple1), pairs(m3_both_types_all_emmeans_simple2)))


# plot
types_emmeans <- data.frame(emmeans(m3_both_types_all, ~ activity | language))



types <- ggplot(types_emmeans, aes(activity, emmean, colour = activity, shape = language, group = language)) + 
  geom_line(aes(group = language)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_shape_manual(values = c(16, 21)) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "grey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Other Child-Cent','Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "Types (rate per min)")

types
ggsave("./figures/emmeans_types_may5_2025.pdf", width = 6, height = 6, units = "in")

```




## MLUw x ACTIVITY - BOTH - ALL TALK - LG as Moderator
```{r}
# singular fit with segment_num as random intercept, so we removed this
m1_both_mlu_all <- lmer(mlu_w2 ~ tokens_hr_child + activity +
                                (1 | id),
                                data = mlu_all_mm, REML = F)

m2_both_mlu_all <- lmer(mlu_w2 ~ tokens_hr_child + language + activity +
                                (1 | id),
                                data = mlu_all_mm, REML = F)

m3_both_mlu_all <- lmer(mlu_w2 ~ tokens_hr_child + (language * activity) +
                                (1 | id),
                                data = mlu_all_mm, REML = F)

# see if adding the intx adds
anova(m1_both_mlu_all, m2_both_mlu_all, m3_both_mlu_all)

# anova table for final model
anova(m2_both_mlu_all)



# emmeans for activity OR language 
m2_both_mlu_all_emmeans_activity <- emmeans(m2_both_mlu_all, ~ activity)

m2_both_mlu_all_emmeans_activity
pairs(m2_both_mlu_all_emmeans_activity)



# emmeans PER language using model WIHTOUT interactions - for figure
m2_both_mlu_all_emmeans_simple1 <- emmeans(m2_both_mlu_all, ~ activity | language)
m2_both_mlu_all_emmeans_simple2 <- emmeans(m2_both_mlu_all, ~ language | activity)

m2_both_mlu_all_emmeans_simple1

# did not use since the interaction was NS
# rbind(pairs(m2_both_mlu_all_emmeans_simple1), pairs(m2_both_mlu_all_emmeans_simple2))
# confint(rbind(pairs(m2_both_mlu_all_emmeans_simple1), pairs(m2_both_mlu_all_emmeans_simple2)))



# plot
mlu_emmeans <- data.frame(emmeans(m2_both_mlu_all, ~ activity | language))


mlu <- ggplot(mlu_emmeans, aes(activity, emmean, colour = activity, shape = language, group = language)) + 
  geom_line(aes(color = activity)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_shape_manual(values = c(16, 21)) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "grey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Other Child-Cent','Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "MLUw")

mlu

ggsave("./figures/emmeans_mlu_may5_2025.pdf", width = 6, height = 6, units = "in")

```




## PROP RESPONSES x ACTIVITY - BOTH - ALL TALK - LG as Moderator
```{r}
m1_both_propresp_all <- lmer(prop_adultresp2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m2_both_propresp_all <- lmer(prop_adultresp2 ~ tokens_hr_child + language + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m3_both_propresp_all <- lmer(prop_adultresp2 ~ tokens_hr_child + (language * activity) +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

# see if adding the intx adds
anova(m1_both_propresp_all, m2_both_propresp_all, m3_both_propresp_all)

# anova table for final model
anova(m3_both_propresp_all)



# emmeans
# interaction - post hoc tests of simple effects
m3_both_propresp_all_emmeans_simple1 <- emmeans(m3_both_propresp_all, ~ activity | language)
m3_both_propresp_all_emmeans_simple2 <- emmeans(m3_both_propresp_all, ~ language | activity)

m3_both_propresp_all_emmeans_simple1


rbind(pairs(m3_both_propresp_all_emmeans_simple1), pairs(m3_both_propresp_all_emmeans_simple2))
confint(rbind(pairs(m3_both_propresp_all_emmeans_simple1), pairs(m3_both_propresp_all_emmeans_simple2)))


# plot
propresp_emmeans <- data.frame(emmeans(m3_both_propresp_all, ~ activity | language))



resp <- ggplot(propresp_emmeans, aes(activity, emmean, colour = activity, shape = language, group = language)) + 
  geom_line(aes(group = language)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_shape_manual(values = c(16, 21)) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "grey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Other Child-Cent','Adult-Cent')) +
  labs(x = "", y = "EMM", title = "Proportion of Responses")

resp

ggsave("./figures/emmeans_resp_may5_2025.pdf", width = 6, height = 6, units = "in")

```




## PROP IMIT/EXP x ACTIVITY - BOTH - ALL TALK - LG as Moderator
```{r}
m1_both_propimitexp_all <- lmer(prop_adult_imitexp2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m2_both_propimitexp_all <- lmer(prop_adult_imitexp2 ~ tokens_hr_child + language + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m3_both_propimitexp_all <- lmer(prop_adult_imitexp2 ~ tokens_hr_child + (language * activity) +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

# see if adding the intx adds
anova(m1_both_propimitexp_all, m2_both_propimitexp_all, m3_both_propimitexp_all)


# anova table for final model
anova(m1_both_propimitexp_all)


# emmeans
m1_both_propimitexp_all_emmeans_activity <- emmeans(m1_both_propimitexp_all, ~ activity)

m1_both_propimitexp_all_emmeans_activity


# emmans per language using model WIHTOUT interactions
m2_both_propimitexp_all_emmeans_simple1 <- emmeans(m2_both_propimitexp_all, ~ activity | language)
m2_both_propimitexp_all_emmeans_simple2 <- emmeans(m2_both_propimitexp_all, ~ language | activity)

m2_both_propimitexp_all_emmeans_simple1


# plot
propimitexp_emmeans <- data.frame(emmeans(m2_both_propimitexp_all, ~ activity | language))


imit_exp <- ggplot(propimitexp_emmeans, aes(activity, emmean, colour = activity, shape = language, group = language)) + 
  geom_line(aes(group = language)) +
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_shape_manual(values = c(16, 21)) + 
  scale_color_manual(values=c("darkviolet", "firebrick1", "grey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Other Child-Cent','Adult-Cent')) +
  labs(x = "", y = "EMM", title = "Proportion of Imitations/Expansions")

imit_exp

ggsave("./figures/emmeans_imit_exp_may5_2025.pdf", width = 6, height = 6, units = "in")

```



# Combining plots
```{r}
# grid all
ggarrange(tokens, types, mlu, resp, imit_exp, common.legend = T, legend = "top")
ggsave("./figures/emmeans_grid_all_line_may5_2025.pdf", width = 14, height = 10, units = "in", dpi = 300)

```


# Models to check child covariate
```{r}
# tokens
anova(m1_both_tokens_all)
anova(m1_both_types_all)
anova(m1_both_mlu_all)
anova(m1_both_propresp_all)
anova(m1_both_propimitexp_all)
```


# Mixed models - 4 categories - HI as Moderator
## TOKENS x ACTIVITY - BOTH - ALL TALK - HI as a moderator
```{r}
# comparing models
m1_both_tokens_all_hi <- lmer(tokens_permin2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m2_both_tokens_all_hi <- lmer(tokens_permin2 ~ tokens_hr_child + hi + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m3_both_tokens_all_hi <- lmer(tokens_permin2 ~ tokens_hr_child + (hi * activity) +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

# see if adding the intx adds
anova(m1_both_tokens_all_hi, m2_both_tokens_all_hi, m3_both_tokens_all_hi)

# anova table for final model
anova(m1_both_tokens_all_hi)
```




## TYPES x ACTIVITY - BOTH - ALL TALK - HI as a moderator
```{r}
# comparing models
m1_both_types_all_hi <- lmer(types_permin2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m2_both_types_all_hi <- lmer(types_permin2 ~ tokens_hr_child + hi + activity +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

m3_both_types_all_hi <- lmer(types_permin2 ~ tokens_hr_child + (hi * activity) +
                                (1 | id) + (1 | segment_num),
                                data = freq_all_mm, REML = F)

# see if adding the intx adds
anova(m1_both_types_all_hi, m2_both_types_all_hi, m3_both_types_all_hi)

# anova table for final model
anova(m1_both_types_all_hi)
```




## MLUw x ACTIVITY - BOTH - ALL TALK - HI as a moderator
```{r}
# singular fit with segment_num as random intercept, so removed this
m1_both_mlu_all_hi <- lmer(mlu_w2 ~ tokens_hr_child + activity +
                                (1 | id),
                                data = mlu_all_mm, REML = F)

m2_both_mlu_all_hi <- lmer(mlu_w2 ~ tokens_hr_child + hi + activity +
                                (1 | id),
                                data = mlu_all_mm, REML = F)

m3_both_mlu_all_hi <- lmer(mlu_w2 ~ tokens_hr_child + (hi * activity) +
                                (1 | id),
                                data = mlu_all_mm, REML = F)

# see if adding the intx adds
anova(m1_both_mlu_all_hi, m2_both_mlu_all_hi, m3_both_mlu_all_hi)

# anova table for final model
anova(m2_both_mlu_all_hi)
```




## PROP RESPONSES x ACTIVITY - BOTH - ALL TALK - HI as a moderator
```{r}
m1_both_propresp_all_hi <- lmer(prop_adultresp2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m2_both_propresp_all_hi <- lmer(prop_adultresp2 ~ tokens_hr_child + hi + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m3_both_propresp_all_hi <- lmer(prop_adultresp2 ~ tokens_hr_child + (hi * activity) +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

# see if adding the intx adds
anova(m1_both_propresp_all_hi, m2_both_propresp_all_hi, m3_both_propresp_all_hi)
```




## PROP IMIT/EXP x ACTIVITY - BOTH - ALL TALK - HI as a moderator
```{r}
# using model removing 1 outlier
m1_both_propimitexp_all_hi <- lmer(prop_adult_imitexp2 ~ tokens_hr_child + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m2_both_propimitexp_all_hi <- lmer(prop_adult_imitexp2 ~ tokens_hr_child + hi + activity +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

m3_both_propimitexp_all_hi <- lmer(prop_adult_imitexp2 ~ tokens_hr_child + (hi * activity) +
                                (1 | id) + (1 | segment_num),
                                data = chip_mm, REML = F)

# see if adding the intx adds
anova(m1_both_propimitexp_all_hi, m2_both_propimitexp_all_hi, m3_both_propimitexp_all_hi)

# anova table for final model
anova(m1_both_propimitexp_all_hi)
```

