---
title: "Regressions - Durations of Activities"
author: "Janet Bang"
date: "November 17, 2022"
output:
  html_document: 
    toc: yes
    toc_float: yes
editor_options: 
  chunk_output_type: console
---

```{r, echo = F}
library(knitr)
opts_chunk$set(echo=TRUE, 
               warning=FALSE, message=FALSE, 
               cache=FALSE)
options(width = 100)

opts_chunk$set(fig.width = 12, fig.height = 12) 
```


This code is for the results to the question: Does what caregivers are doing predict how much they engage with their target children? 



### Load libraries and set theme
```{r}
library(tidyverse)
library(Hmisc)
library(GGally)
library(ppcor)
library(gridExtra)
library(psych)
library(sjPlot)
library(stargazer)

theme_set(theme_bw())
```


## Read in data
```{r}
# demographics
demo_english <- read_csv("./data_demo_lena_transcripts/demo_english_ms.csv") %>% 
  rename(id = ID, hi = HI24Final, momed = Momed) %>% 
  dplyr::select(id, hi, momed) %>% 
  mutate(id = as.character(id), 
         language = "english")

demo_spanish <- read_csv("./data_demo_lena_transcripts/demo_spanish_ms.csv") %>% 
  rename(id = ID, hi = HI_18, momed = MomEd_25m) %>% 
  dplyr::select(id, hi, momed) %>% 
  mutate(id = as.character(id), 
         language = "spanish")

demo <- rbind(demo_english, demo_spanish)


# freq
# sum across segments, so there are only up to 4 data points per child (1 for each activity group)
freq_reg <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  filter(activity != "kwalods", 
         speech == "all") %>% 
  mutate(activity = recode(activity, "play" = "cc", "conv" = "cc", 
                           "food" = "cc", "routines" = "cc", "gemods" = "non_tcds")) %>% 
  mutate(id = factor(id), 
         language = factor(language)) %>% 
  group_by(id, activity, speaker) %>% # not grouping by segment number because looking across the whole tCDS hour
  mutate(tokens_total_4act = sum(tokens), 
         types_total_4act = sum(types), 
         dur_min_4act = sum(dur_min)) %>% 
  distinct(id, activity, language, speaker, tokens_total_4act, types_total_4act, dur_min_4act) %>% 
  ungroup() %>% 
  mutate(activity = factor(activity, levels = c("books", "cc", "ac", "non_tcds"))) 
```


## Create dfs for ADULTS and CHI
```{r}
# subset for adult and child
freq_reg_adults <- freq_reg %>% 
  filter(speaker == "ADULTS")

freq_reg_child <- freq_reg %>% 
  filter(speaker == "CHI")

str(freq_reg_adults)
str(freq_reg_child)
```


## Create tokens rate per hour - Children
```{r}
freq_hr_child <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  dplyr::select(-X1) %>% 
  filter(speech == "all", 
         speaker == "CHI") %>% 
  group_by(id) %>% 
  mutate(tokens_sum_child = sum(tokens), 
         dur_hr = sum(dur_min)/60, 
         tokens_hr_child = tokens_sum_child/dur_hr) %>% 
  distinct(id, language, tokens_hr_child) %>% 
  ungroup() %>% 
  mutate(id = as.character(id))
```


## Create wide df for regressions with 0s
```{r}
# freq adult
freq_reg_adults_wide <- freq_reg_adults %>% 
  ungroup() %>% 
  group_by(id) %>% 
  mutate(tokens_sum_adult = sum(tokens_total_4act), 
         dur_hr = sum(dur_min_4act)/60, 
         tokens_hr_adult = tokens_sum_adult/dur_hr) %>% 
  full_join(freq_hr_child, by = c("id", "language")) %>% 
  distinct(id, activity, language, dur_min_4act, tokens_hr_adult, tokens_hr_child) %>% 
  spread(activity, dur_min_4act) %>% 
  replace_na(list(books = 0, cc = 0, ac = 0, non_tcds = 0)) %>% 
  mutate(br_group = ifelse(books == 0, 0, 1), 
         br_group = as.factor(br_group))


psych::describe(freq_reg_adults_wide$tokens_hr_adult)
```


## Descriptives
```{r}
# descriptives
hist(freq_reg_adults_wide$books)
hist(freq_reg_adults_wide$cc)
hist(freq_reg_adults_wide$ac)
hist(freq_reg_adults_wide$non_tcds)


# difference between families who BR vs. non
ggplot(freq_reg_adults_wide, aes(x = br_group, y = tokens_hr_adult)) + 
  geom_boxplot() + 
  geom_jitter(alpha = .5)

# t-tests
t.test(tokens_hr_adult ~ br_group, 
       data = freq_reg_adults_wide, var.equal = TRUE)
```


## Regressions (Full sample) - books* + cc* + ac + non-tCDS
```{r}
# freq_reg_adults_wide_rmoutlier <- freq_reg_adults_wide %>% 
#   filter(id != 20056 & id != 7412)
# nrow(freq_reg_adults_wide_rmoutlier)

# models with tokens
m1 <- lm(tokens_hr_adult ~ tokens_hr_child, 
         data = freq_reg_adults_wide)
m2 <- lm(tokens_hr_adult ~ tokens_hr_child + language, 
         data = freq_reg_adults_wide)
m3 <- lm(tokens_hr_adult ~ tokens_hr_child + language + books,
         data = freq_reg_adults_wide)
m4 <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc,
         data = freq_reg_adults_wide)
m5 <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc + ac,
         data = freq_reg_adults_wide)
m6 <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc + ac + non_tcds,
         data = freq_reg_adults_wide)

anova(m1, m2, m3, m4, m5, m6)
summary(m4)


# checking if language is a moderator
m4 <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc,
         data = freq_reg_adults_wide)
m4_intx1 <- lm(tokens_hr_adult ~ tokens_hr_child + (language * books) + cc,
         data = freq_reg_adults_wide)
m4_intx2 <- lm(tokens_hr_adult ~ tokens_hr_child + (language * books) + (language * cc),
         data = freq_reg_adults_wide)

anova(m4, m4_intx1, m4_intx2)
summary(m4_intx1)



# # check on potential outlier - removing these didn't change pattern of findings
# # 20056 - possibly bc high densest hour; 7412 - less clear, but does have 3rd highest cc value
# cooksd <- cooks.distance(m4)
# View(cooksd)
# influential <- as.numeric(names(cooksd)[(cooksd > 4*mean(cooksd, na.rm=T))])  # influential row numbers
# inf_df <- head(freq_reg_adults_wide_rmoutlier[influential, ])  # influential observations
# View(inf_df)


# table
stargazer(m1, m2, m3, m4, type = "text",
         star.char = c(".","*","**","***"),
         star.cutoffs = c(.1, .05, .01, .001),
         notes = c(". p<0.1; * p<0.05; ** p<0.01; *** p<0.001"),
         notes.append = F,
         digits = 3,
         dep.var.labels = c("Word Tokens in the Densest hour"),
         covariate.labels=c("Child Tokens per Hour", "Language Group",
                            "Book Sharing (min)",
                            "Other-Child-Centered Activities (min)"))

# diagnostics
plot_model(m4, type = "diag")
```


## Regressions (Full sample) - cc + books* + ac + non-tCDS
```{r}
# models with tokens and cc before book sharing - cc doesn't add before book sharing
m3.cc <- lm(tokens_hr_adult ~ tokens_hr_child + language + cc,
         data = freq_reg_adults_wide)

anova(m1, m2, m3.cc, m4, m5, m6)
summary(m3.cc)
summary(m4)
summary(m6)
```



## Regressions (Full sample) - books* + cc* + non-tCDS + ac; AC does not add above non-tCDS
```{r}
m5.ods <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc + non_tcds,
         data = freq_reg_adults_wide)

anova(m1, m2, m3, m4, m5.ods, m6)
```



## Regressions (BR only families) - books* + cc + ac + non-tCDS; same if switch cc and books
```{r}
# models with ONLY BR families
bronly_tokens <- freq_reg_adults_wide %>% 
  filter(br_group == 1)


# regressions
m1.bronly <- lm(tokens_hr_adult ~ tokens_hr_child, 
         data = bronly_tokens)
m2.bronly <- lm(tokens_hr_adult ~ tokens_hr_child + language,
         data = bronly_tokens)
m3.bronly <- lm(tokens_hr_adult ~ tokens_hr_child + language + books,
         data = bronly_tokens)
m4.bronly <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc,
         data = bronly_tokens)
m5.bronly <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc + ac,
         data = bronly_tokens)
m6.bronly <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc + ac + non_tcds,
         data = bronly_tokens)

anova(m1.bronly, m2.bronly, m3.bronly, m4.bronly, m5.bronly, m6.bronly)
summary(m3.bronly)



# checking if language is a moderator
m3.bronly_intx <- lm(tokens_hr_adult ~ tokens_hr_child + (language * books),
         data = bronly_tokens)
anova(m3.bronly, m3.bronly_intx)


# table
stargazer(m1.bronly, m2.bronly, m3.bronly, type = "text",
         star.char = c(".","*","**","***"),
         star.cutoffs = c(.1, .05, .01, .001),
         notes = c(". p<0.1; * p<0.05; ** p<0.01; *** p<0.001"),
         notes.append = F,
         digits = 3,
         dep.var.labels = c("Word Tokens in the Densest hour"),
         covariate.labels=c("Child Tokens per Hour", "Language Group",
                            "Book Sharing (min)"))


# plot model
plot_model(m3.bronly, type = "pred", terms = c("books"),
           show.data = T,
           dot.size = 4, 
           colors = "darkviolet") +
  aes(color = group) + 
  font_size(axis_title.x = 25, axis_title.y = 25, labels.x = 18, labels.y = 18) + 
  labs(x = "Book Sharing Duration (min)", y = "Caregiver\nTotal Word Tokens\n(Densest tCDS Hour)", title = "") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5), 
        legend.position = "none")
ggsave("./figures/balloon_bronly.pdf", width = 12, height = 8, units = "in", dpi = 300)




# model with ONLY BR families and cc first
m3.bronly.cc <- lm(tokens_hr_adult ~ tokens_hr_child + language + cc,
         data = bronly_tokens)

anova(m1.bronly, m2.bronly, m3.bronly.cc, m4.bronly, m5.bronly, m6.bronly)


# model with ONLY BR families and non_tCDS above ac
m5.bronly.ods <- lm(tokens_hr_adult ~ tokens_hr_child + language + books + cc + non_tcds,
         data = bronly_tokens)

anova(m1.bronly, m2.bronly, m3.bronly, m4.bronly, m5.bronly.ods, m6.bronly)



# diagnostics
plot_model(m3.bronly, type = "diag")
```



## Regressions (NON BR only families) - cc* + ac + gemods; same if switch cc and books
```{r}
# models with NON BR families
nonbr_tokens <- freq_reg_adults_wide %>% 
  filter(br_group == 0)

# regressions
m1.nonbr <- lm(tokens_hr_adult ~ tokens_hr_child, 
         data = nonbr_tokens)
m2.nonbr <- lm(tokens_hr_adult ~ tokens_hr_child + language,
         data = nonbr_tokens)
m3.nonbr <- lm(tokens_hr_adult ~ tokens_hr_child + language + cc,
         data = nonbr_tokens)
m4.nonbr <- lm(tokens_hr_adult ~ tokens_hr_child + language + cc + ac,
         data = nonbr_tokens)
m5.nonbr <- lm(tokens_hr_adult ~ tokens_hr_child + language + cc + ac + non_tcds,
         data = nonbr_tokens)

anova(m1.nonbr, m2.nonbr, m3.nonbr, m4.nonbr, m5.nonbr)
summary(m3.nonbr)
summary(m4.nonbr)


# checking if language is a moderator
m3.nonbr_intx <- lm(tokens_hr_adult ~ tokens_hr_child + (language * cc),
         data = nonbr_tokens)
anova(m3.nonbr, m3.nonbr_intx)


# table
stargazer(m1.nonbr, m2.nonbr, m3.nonbr, m4.nonbr, type = "text",
         star.char = c(".","*","**","***"),
         star.cutoffs = c(.1, .05, .01, .001),
         notes = c(". p<0.1; * p<0.05; ** p<0.01; *** p<0.001"),
         notes.append = F,
         digits = 3,
         dep.var.labels = c("Word Tokens in the Densest hour"),
         covariate.labels=c("Child Tokens per Hour", "Language Group",
                            "Other Child-Centered Activities (min)", 
                            "Adult-Centered Activities (min)"))



# plot model
plot_model(m3.nonbr, type = "pred", terms = c("cc"),
           show.data = T,
           dot.size = 4,
           colors = "firebrick1") +
  aes(color = group) + 
  font_size(axis_title.x = 25, axis_title.y = 25, labels.x = 18, labels.y = 18) + 
  labs(x = "Other Child-Centered Duration (min)", y = "Caregiver\nTotal Word Tokens\n(Densest tCDS Hour)", title = "") +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5), 
        legend.position = "none")
ggsave("./figures/balloon_nonbronly.pdf", width = 12, height = 8, units = "in", dpi = 300)



# model with NON BR families and ac above cc; p = .06
m3.nonbr.ac <- lm(tokens_hr_adult ~ tokens_hr_child + language + ac,
         data = nonbr_tokens)

anova(m1.nonbr, m2.nonbr, m3.nonbr.ac, m4.nonbr, m5.nonbr)
summary(m4.nonbr)



# model with NON BR families and gemods above ac
m4.nonbr.ods <- lm(tokens_hr_adult ~ tokens_hr_child + language + cc + non_tcds,
         data = nonbr_tokens)

anova(m1.nonbr, m2.nonbr, m3.nonbr, m4.nonbr.ods, m5.nonbr)


# correlations
ggplot(nonbr_tokens, aes(cc, ac, color = language)) + 
  geom_point() + 
  geom_smooth(method = "lm")

cor.test(nonbr_tokens$cc, nonbr_tokens$ac)


# diagnostics
plot_model(m3.nonbr, type = "diag")

```

