---
title: "Interrater Reliability"
author: "Janet Bang"
date: "November 17, 2022"
output:
  html_document: 
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


This is code of the inter-rater reliability between first and second coders when determining 1) the tCDS activity of the caregiver-child interaction and 2) the duration of the tCDS activity. 



## Load libraries
```{r}
library(tidyverse)
library(irr)
library(psych)
library(gridExtra)

theme_set(theme_bw())
```



## Read in data
```{r}
ir_en_6categ <- read_csv("./data_reliability/ir_en_6categ_wide.csv")
ir_sp_6categ <- read_csv("./data_reliability/ir_sp_6categ_wide.csv")
```



## See number of codes for each coder
```{r}
# english
ir_en_6categ %>%
  select(-coder2_ant) %>% 
  filter(coder1_ant != "no_code") %>% 
  nrow()

ir_en_6categ %>%
  select(-coder1_ant) %>% 
  filter(coder2_ant != "no_code") %>% 
  nrow()



# spanish
ir_sp_6categ %>%
  select(-coder2_ant) %>% 
  filter(coder1_ant != "no_code") %>% 
  nrow()

ir_sp_6categ %>%
  select(-coder1_ant) %>% 
  filter(coder2_ant != "no_code") %>% 
  nrow()
```



## Create dfs that use coder1 as a reference (excluding rows where coder1 = "no_code")
```{r}
# this creates a warning message that we can ignore 
# Warning message:
#Problem with `mutate()` input `coder2_dur`.
#ℹ NAs introduced by coercion
#ℹ Input `coder2_dur` is `as.numeric(coder2_dur)`. 

ir_en_6categ_ref <- ir_en_6categ %>%
  filter(coder1_ant != "no_code") %>% 
  mutate(match = ifelse(coder1_ant == coder2_ant, "match", "no_match")) %>% 
  mutate(coder1_dur = as.numeric(coder1_dur), 
         coder2_dur = as.numeric(coder2_dur)) %>% 
  mutate(coder1_dur = replace_na(coder1_dur, 0),
         coder2_dur = replace_na(coder2_dur, 0)) 

ir_sp_6categ_ref <- ir_sp_6categ %>%
  filter(coder1_ant != "no_code") %>% 
  mutate(match = ifelse(coder1_ant == coder2_ant, "match", "no_match")) %>% 
  mutate(coder1_dur = as.numeric(coder1_dur), 
         coder2_dur = as.numeric(coder2_dur)) %>% 
  mutate(coder1_dur = replace_na(coder1_dur, 0),
         coder2_dur = replace_na(coder2_dur, 0))
```


## See number of removed codes for coder1
```{r}
ir_en_6categ %>%
  filter(coder1_ant == "no_code") %>% 
  nrow()

ir_sp_6categ %>%
  filter(coder1_ant == "no_code") %>% 
  nrow()
```




## Proportion of matched codes between coder1 and coder2 - Overall
```{r}
# english
match_en <- ir_en_6categ_ref %>% 
  filter(match == "match")

nrow(match_en)
nrow(ir_en_6categ_ref)
nrow(match_en) / nrow(ir_en_6categ_ref)


# spanish
match_sp <- ir_sp_6categ_ref %>% 
  filter(match == "match")

nrow(match_sp)
nrow(ir_sp_6categ_ref)
nrow(match_sp) / nrow(ir_sp_6categ_ref)
```



## Proportion of matched codes between coder1 and coder2 - English per category
```{r}
# english
# books
match_books_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "books" & match == "match")

books_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "books")

nrow(match_books_en)
nrow(books_en)
nrow(match_books_en) / nrow(books_en)

# play
match_play_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "play" & match == "match")

play_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "play")

nrow(match_play_en)
nrow(play_en)
nrow(match_play_en) / nrow(play_en)


# food
match_food_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "food" & match == "match")

food_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "food")

nrow(match_food_en) 
nrow(food_en)
nrow(match_food_en) / nrow(food_en)


# routines
match_routines_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "routines" & match == "match")

routines_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "routines")

nrow(match_routines_en)
nrow(routines_en)
nrow(match_routines_en) / nrow(routines_en)


# unstructured conversation
match_conv_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "conv" & match == "match")

conv_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "conv")

nrow(match_conv_en)
nrow(conv_en)
nrow(match_conv_en) / nrow(conv_en)


# adult-centered interaction
match_adultcent_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "ac" & match == "match")

adultcent_en <- ir_en_6categ_ref %>% 
  filter(coder1_ant == "ac")

nrow(match_adultcent_en)
nrow(adultcent_en)
nrow(match_adultcent_en) / nrow(adultcent_en)
```


## Proportion of matched codes between coder1 and coder2 - Spanish per category
```{r}
# spanish
# books
match_books_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "books" & match == "match")

books_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "books")

nrow(match_books_sp)
nrow(books_sp)
nrow(match_books_sp) / nrow(books_sp)


# play
match_play_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "play" & match == "match")

play_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "play")

nrow(match_play_sp)
nrow(play_sp)
nrow(match_play_sp) / nrow(play_sp)


# food
match_food_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "food" & match == "match")

food_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "food")

nrow(match_food_sp)
nrow(food_sp)
nrow(match_food_sp) / nrow(food_sp)


# routines
match_routines_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "routines" & match == "match")

routines_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "routines")

nrow(match_routines_sp)
nrow(routines_sp)
nrow(match_routines_sp) / nrow(routines_sp)


# unstructured conversation
match_conv_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "conv" & match == "match")

conv_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "conv")

nrow(match_conv_sp)
nrow(conv_sp)
nrow(match_conv_sp) / nrow(conv_sp)


# adult-centered interaction
match_adultcent_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "ac" & match == "match")

adultcent_sp <- ir_sp_6categ_ref %>% 
  filter(coder1_ant == "ac")

nrow(match_adultcent_sp)
nrow(adultcent_sp)
nrow(match_adultcent_sp) / nrow(adultcent_sp)
```


## Kappa
```{r}
# we do not want weighted kappa; this takes into account disagreements, but weighted kappa is more relevant when data are rank ordered
ir_en_6categ_kappa <- ir_en_6categ_ref %>% 
  select(c(coder1_ant, coder2_ant))

cohen.kappa(as.matrix(ir_en_6categ_kappa))
kappa2(ir_en_6categ_kappa)


ir_sp_6categ_kappa <- ir_sp_6categ_ref %>% 
  select(c(coder1_ant, coder2_ant))

cohen.kappa(as.matrix(ir_sp_6categ_kappa))
kappa2(ir_sp_6categ_kappa)

```



### ICCs
## Create separate dataframes per activity
```{r}
# english
ir_en_books <- ir_en_6categ_ref %>%
  filter(activity_both == "books")

ir_en_play <- ir_en_6categ_ref %>%
  filter(activity_both == "play")

ir_en_food <- ir_en_6categ_ref %>%
  filter(activity_both == "food")

ir_en_routines <- ir_en_6categ_ref %>%
  filter(activity_both == "routines")

ir_en_convo <- ir_en_6categ_ref %>%
  filter(activity_both == "conv")

ir_en_ac <- ir_en_6categ_ref %>%
  filter(activity_both == "ac")



# spanish
ir_sp_books <- ir_sp_6categ_ref %>%
  filter(activity_both == "books")

ir_sp_play <- ir_sp_6categ_ref %>%
  filter(activity_both == "play")

ir_sp_food <- ir_sp_6categ_ref %>%
  filter(activity_both == "food")

ir_sp_routines <- ir_sp_6categ_ref %>%
  filter(activity_both == "routines")

ir_sp_convo <- ir_sp_6categ_ref %>%
  filter(activity_both == "conv")

ir_sp_ac <- ir_sp_6categ_ref %>%
  filter(activity_both == "ac")
```


### Check the number of rows by first coder
```{r}
ir_en_6categ_ref %>% 
  dplyr::select(id, coder1_ant) %>% 
  group_by(coder1_ant) %>% 
  count(coder1_ant) %>% 
  ungroup() %>% 
  mutate(prop = n/sum(n))


ir_sp_6categ_ref %>% 
  dplyr::select(id, coder1_ant) %>% 
  group_by(coder1_ant) %>% 
  count(coder1_ant) %>% 
  ungroup() %>% 
  mutate(prop = n/sum(n))
```



### ICCs
```{r}
# model = the design is not fully crossed since not all coders coded all subject, so we will use a one-way model
# type = agreement bc we care about the absolute value, not rank order)
# unit = default is individual, which is used when a subset of subjects has multiple raters and reliability of rating is meant to generalize to subjects rated by one coder


# english
books_en <- ir_en_books %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(books_en, model = "oneway", type = "agreement")

play_en <- ir_en_play %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(play_en, model = "oneway", type = "agreement")

food_en <- ir_en_food %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(food_en, model = "oneway", type = "agreement")

routines_en <- ir_en_routines %>% 
  # filter(id != 20113) %>% # this participant has coder1_dur dur at 21s and coder2_dur dur at 181s
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(routines_en, model = "oneway", type = "agreement")

convo_en <- ir_en_convo %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(convo_en, model = "oneway", type = "agreement")

ac_en <- ir_en_ac %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(ac_en, model = "oneway", type = "agreement")




# spanish
books_sp <- ir_sp_books %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(books_sp, model = "oneway", type = "agreement")

play_sp <- ir_sp_play %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(play_sp, model = "oneway", type = "agreement")

food_sp <- ir_sp_food %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(food_sp, model = "oneway", type = "agreement")

routines_sp <- ir_sp_routines %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(routines_sp, model = "oneway", type = "agreement")

convo_sp <- ir_sp_convo %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(convo_sp, model = "oneway", type = "agreement")

ac_sp <- ir_sp_ac %>% 
  filter(match == "match") %>%
  select(c(coder1_dur, coder2_dur))
icc(ac_sp, model = "oneway", type = "agreement")

```


## Correlations - not corrected for chance agreement
```{r}
cor.test(books_en$coder1_dur, books_en$coder2_dur)
cor.test(play_en$coder1_dur, play_en$coder2_dur)
cor.test(food_en$coder1_dur, food_en$coder2_dur)
cor.test(routines_en$coder1_dur, routines_en$coder2_dur)
cor.test(convo_en$coder1_dur, convo_en$coder2_dur)
cor.test(ac_en$coder1_dur, ac_en$coder2_dur)


cor.test(books_sp$coder1_dur, books_sp$coder2_dur)
cor.test(play_sp$coder1_dur, play_sp$coder2_dur)
cor.test(food_sp$coder1_dur, food_sp$coder2_dur)
cor.test(routines_sp$coder1_dur, routines_sp$coder2_dur)
cor.test(convo_sp$coder1_dur, convo_sp$coder2_dur)
cor.test(ac_sp$coder1_dur, ac_sp$coder2_dur)
```



### Plots
```{r}
en1 <- ggplot(ir_en_books, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
en2 <- ggplot(ir_en_play, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
en3 <- ggplot(ir_en_food, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
en4 <- ggplot(ir_en_routines, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
en5 <- ggplot(ir_en_convo, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
en6 <- ggplot(ir_en_ac, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")


sp1 <- ggplot(ir_sp_books, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
sp2 <- ggplot(ir_sp_play, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
sp3 <- ggplot(ir_sp_food, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
sp4 <- ggplot(ir_sp_routines, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
sp5 <- ggplot(ir_sp_convo, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")
sp6 <- ggplot(ir_sp_ac, aes(coder1_dur, coder2_dur)) + 
  geom_point() + 
  geom_smooth(method = "lm") + 
  theme(text = element_text(size = 18)) + 
  labs(x = "", y = "")

pdf("./figures/corr_reliability.pdf", width = 20, height = 9) # Open a new pdf file
grid.arrange(en1, en2, en3, en4, en5, en6, 
             sp1, sp2, sp3, sp4, sp5, sp6, ncol = 6) # Write the grid.arrange in the file
dev.off()
```