---
title: "Caregiver Speech Mixed Models - 7 categories; English and Spanish Separately"
author: "Janet Bang"
date: "November 17, 2022"
output:
  html_document: 
   toc: true
   toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r, echo = F}
library(knitr)
opts_chunk$set(echo=TRUE, 
               warning=FALSE, message=FALSE, 
               cache=FALSE)
options(width = 100)

opts_chunk$set(fig.width = 12, fig.height = 8) 
```


This code is for the results to the question, "Do features of caregiver verbal engagement vary as a function of language group and activity?", but conducts analyses separately per language and for separate levels for all other-child-centered activities (see pre-registration here: https://osf.io/byjfg/).



### Load libraries and set theme
```{r}
library(tidyverse)
library(ggpubr)
library(psych)
library(lme4)
library(lmerTest)
library(emmeans)
library(sjPlot)
library(ggeffects)

theme_set(theme_bw())

get_legend<-function(myggplot){
  tmp <- ggplot_gtable(ggplot_build(myggplot))
  leg <- which(sapply(tmp$grobs, function(x) x$name) == "guide-box")
  legend <- tmp$grobs[[leg]]
  return(legend)
}
```


# Read in data and convert
```{r}
# demographics
demo_english <- read_csv("./data_demo_lena_transcripts/demo_english_ms.csv") %>% 
  rename(id = ID, hi = HI24Final, momed = Momed) %>% 
  dplyr::select(id, hi, momed) %>% 
  mutate(id = as.character(id), 
         language = "english")

demo_spanish <- read_csv("./data_demo_lena_transcripts/demo_spanish_ms.csv") %>% 
  rename(id = ID, hi = HI_18, momed = MomEd_25m) %>% 
  dplyr::select(id, hi, momed) %>% 
  mutate(id = as.character(id), 
         language = "spanish")


# NOTE about periods of non-tCDCS
# gemods refers to when there are designated start/end periods of other-directed speech (ODS); this was captured using gems (@G) using CHAT conventions
# kwalods refers to when ODS was transcribed at an utterance-level within a tCDS activity period between caregiver and child (e.g., other-directed speech in the background); this was captured per utterances using CHAT postcodes
## for tokens/min and types/min, we do not include ODS that occurred within a period of tCDS, because durations were captured by activity and not by utterance
## for mlu, we include all ODS across gemods and kwalods


# NOTE about speech == "all"
# "speech" includes two levels: all, spont
# all = refers to all speech by caregivers
# spont = refers to only speech by caregivers that was considered spontaneous rather than recited (e.g., reading book text, singing memorized common songs like itsy bitsy spider); therefore, 'spont' is a subset of 'all'


# freq
freq <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  filter(activity != "kwalods", 
         speech == "all") %>% 
  mutate(activity = recode(activity, "gemods" = "non_tcds")) %>% 
  mutate(id = factor(id), 
         language = factor(language),
         activity = factor(activity, levels = c("books", "play", "food", 
                                                "routines", "conv", "ac", "non_tcds")))


# mlu
mlu <- read_csv("./data_demo_lena_transcripts/mlu.csv") %>% 
  filter(speech == "all") %>% 
  mutate(activity = recode(activity, "ods" = "non_tcds")) %>% 
  mutate(id = factor(id), 
         language = factor(language),
         activity = factor(activity, levels = c("books", "play", "food", 
                                                "routines", "conv", "ac", "non_tcds")))


# chip
# this includes only caregivers, therefore there is no speaker column
# we exclude periods of ODS because this is about responsiveness to the child during periods of tCDS
chip <- read_csv("./data_demo_lena_transcripts/chip.csv") %>% 
  filter(activity != "ods") %>% 
  mutate(id = factor(id), 
         language = factor(language),
         activity = factor(activity, levels = c("books", "play", "food", 
                                                "routines", "conv", "ac", "non_tcds")))
  

str(freq)
str(mlu)
str(chip)
```




## Create dfs for ADULTS and CHI
```{r}
# FREQ
freq_adult_en <- freq %>% 
  filter(speaker == "ADULTS") %>% 
  filter(language == "english")

freq_adult_sp <- freq %>% 
  filter(speaker == "ADULTS") %>% 
  filter(language == "spanish")


# MLU
mlu_adult_en <- mlu %>% 
  filter(speaker == "ADULTS") %>% 
  filter(language == "english")

mlu_adult_sp <- mlu %>% 
  filter(speaker == "ADULTS") %>% 
  filter(language == "spanish")
```



# Prep data for mixed models
## Create tokens rate per hour - Children
```{r}
freq_hr_child <- read_csv("./data_demo_lena_transcripts/freq.csv") %>% 
  dplyr::select(-X1) %>% 
  filter(speech == "all", 
         speaker == "CHI") %>% 
  group_by(id) %>% 
  mutate(tokens_sum_child = sum(tokens), 
         dur_hr = sum(dur_min)/60, 
         tokens_hr_child = tokens_sum_child/dur_hr) %>% 
  distinct(id, language, tokens_hr_child) %>% 
  ungroup() %>% 
  mutate(id = as.character(id))

# per language
freq_hr_child_en <- freq_hr_child %>% filter(language == "english")
freq_hr_child_sp <- freq_hr_child %>% filter(language == "spanish")
```




## Merge freq_adult, child tokens per hour, and demographic info
```{r}
# freq
freq_all_mm_en <- freq_adult_en %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child_en, by = c("id", "language")) %>% 
  left_join(demo_english, by = c("id", "language"))

freq_all_mm_sp <- freq_adult_sp %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child_sp, by = c("id", "language")) %>% 
  left_join(demo_spanish, by = c("id", "language"))



# mlu
mlu_all_mm_en <- mlu_adult_en %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child_en, by = c("id", "language")) %>% 
  left_join(demo_english, by = c("id", "language"))

mlu_all_mm_sp <- mlu_adult_sp %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child_sp, by = c("id", "language")) %>% 
  left_join(demo_spanish, by = c("id", "language"))



# chip
chip_mm_en <- chip %>% 
  filter(language == "english") %>% 
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child_en, by = c("id", "language")) %>% 
  left_join(demo_english, by = c("id", "language"))

chip_mm_sp <- chip %>% 
  filter(language == "spanish") %>%  
  mutate(id = as.character(id)) %>% 
  left_join(freq_hr_child_sp, by = c("id", "language")) %>% 
  left_join(demo_spanish, by = c("id", "language"))

```



# Mixed models - 7 categories
## TOKENS x ACTIVITY - ENGLISH - ALL TALK
```{r}
# comparing models
m1_english_tokens_all <- lmer(tokens_permin ~ tokens_hr_child + 
                                (1 | id),
                                data = freq_all_mm_en, REML = F)

m2_english_tokens_all <- lmer(tokens_permin ~ tokens_hr_child + activity +
                                (1 | id),
                                data = freq_all_mm_en, REML = F)

# see if adding the intx adds
anova(m1_english_tokens_all, m2_english_tokens_all)

# anova table for final model
anova(m2_english_tokens_all)


# emmeans
m2_english_tokens_all_emmeans_activity <- emmeans(m2_english_tokens_all, ~ activity)

m2_english_tokens_all_emmeans_activity
pairs(m2_english_tokens_all_emmeans_activity)


# plot
tokens_emmeans_en <- data.frame(emmeans(m2_english_tokens_all, ~ activity))


tokens_en <- ggplot(tokens_emmeans_en, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black"),
                     name="Activity",
                     labels=c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "English - Tokens (rate per min)")


tokens_en

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_english_tokens_all, type = "diag") 
```


## TOKENS x ACTIVITY - SPANISH - ALL TALK
```{r}
# comparing models
m1_spanish_tokens_all <- lmer(tokens_permin ~ tokens_hr_child + 
                                (1 | id),
                                data = freq_all_mm_sp, REML = F)

m2_spanish_tokens_all <- lmer(tokens_permin ~ tokens_hr_child + activity +
                                (1 | id),
                                data = freq_all_mm_sp, REML = F)

# see if adding the intx adds
anova(m1_spanish_tokens_all, m2_spanish_tokens_all)

# anova table for final model
anova(m2_spanish_tokens_all)


# emmeans
m2_spanish_tokens_all_emmeans_activity <- emmeans(m2_spanish_tokens_all, ~ activity)

m2_spanish_tokens_all_emmeans_activity
pairs(m2_spanish_tokens_all_emmeans_activity)


# plot
tokens_emmeans_sp <- data.frame(emmeans(m2_spanish_tokens_all, ~ activity))


tokens_sp <- ggplot(tokens_emmeans_sp, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black"),
                     name="Activity",
                     labels=c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "Spanish - Tokens (rate per min)")


tokens_sp

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_spanish_tokens_all, type = "diag") 
```


## TYPES x ACTIVITY - ENGLISH - ALL TALK
```{r}
# comparing models
m1_english_types_all <- lmer(types_permin ~ tokens_hr_child + 
                                (1 | id),
                                data = freq_all_mm_en, REML = F)

m2_english_types_all <- lmer(types_permin ~ tokens_hr_child + activity +
                                (1 | id),
                                data = freq_all_mm_en, REML = F)

# see if adding the intx adds
anova(m1_english_types_all, m2_english_types_all)

# anova table for final model
anova(m2_english_types_all)



# emmeans
m2_english_types_all_emmeans_activity <- emmeans(m2_english_types_all, ~ activity)

m2_english_types_all_emmeans_activity
pairs(m2_english_types_all_emmeans_activity)


# plot
types_emmeans_en <- data.frame(emmeans(m2_english_types_all, ~ activity))


types_en <- ggplot(types_emmeans_en, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "English - Types (rate per min)")

types_en

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_english_types_all, type = "diag")
```


## TYPES x ACTIVITY - SPANISH - ALL TALK
```{r}
# comparing models
m1_spanish_types_all <- lmer(types_permin ~ tokens_hr_child + 
                                (1 | id),
                                data = freq_all_mm_sp, REML = F)

m2_spanish_types_all <- lmer(types_permin ~ tokens_hr_child + activity +
                                (1 | id),
                                data = freq_all_mm_sp, REML = F)

# see if adding the intx adds
anova(m1_spanish_types_all, m2_spanish_types_all)

# anova table for final model
anova(m2_spanish_types_all)



# emmeans
m2_spanish_types_all_emmeans_activity <- emmeans(m2_spanish_types_all, ~ activity)

m2_spanish_types_all_emmeans_activity
pairs(m2_spanish_types_all_emmeans_activity)


# plot
types_emmeans_sp <- data.frame(emmeans(m2_spanish_types_all, ~ activity))


types_sp <- ggplot(types_emmeans_sp, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "Spanish - Types (rate per min)")

types_sp

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_spanish_types_all, type = "diag")
```



## MLUw x ACTIVITY - ENGLISH - ALL TALK
```{r}
# comparing models
m1_english_mlu_all <- lmer(mlu_w ~ tokens_hr_child + 
                                (1 | id),
                                data = mlu_all_mm_en, REML = F)

m2_english_mlu_all <- lmer(mlu_w ~ tokens_hr_child + activity +
                                (1 | id),
                                data = mlu_all_mm_en, REML = F)

# see if adding the intx adds
anova(m1_english_mlu_all, m2_english_mlu_all)

# anova table for final model
anova(m2_english_mlu_all)



# emmeans
m2_english_mlu_all_emmeans_activity <- emmeans(m2_english_mlu_all, ~ activity)

m2_english_mlu_all_emmeans_activity
pairs(m2_english_mlu_all_emmeans_activity)


# plot
mlu_emmeans_en <- data.frame(emmeans(m2_english_mlu_all, ~ activity))


mlu_en <- ggplot(mlu_emmeans_en, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "English - MLUw")

mlu_en


# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_english_mlu_all, type = "diag")
```



## MLUw x ACTIVITY - SPANISH - ALL TALK
```{r}
# comparing models
m1_spanish_mlu_all <- lmer(mlu_w ~ tokens_hr_child + 
                                (1 | id),
                                data = mlu_all_mm_sp, REML = F)

m2_spanish_mlu_all <- lmer(mlu_w ~ tokens_hr_child + activity +
                                (1 | id),
                                data = mlu_all_mm_sp, REML = F)

# see if adding the intx adds
anova(m1_spanish_mlu_all, m2_spanish_mlu_all)

# anova table for final model
anova(m2_spanish_mlu_all)



# emmeans
m2_spanish_mlu_all_emmeans_activity <- emmeans(m2_spanish_mlu_all, ~ activity)

m2_spanish_mlu_all_emmeans_activity
pairs(m2_spanish_mlu_all_emmeans_activity)


# plot
mlu_emmeans_sp <- data.frame(emmeans(m2_spanish_mlu_all, ~ activity))


mlu_sp <- ggplot(mlu_emmeans_sp, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey", "black")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent', 'non-tCDS')) +
  labs(x = "", y = "EMM", title = "Spanish - MLUw")

mlu_sp


# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_spanish_mlu_all, type = "diag")
```


## PROP RESPONSES x ACTIVITY - ENGLISH - ALL TALK
```{r}
# comparing models
m1_english_propresp_all <- lmer(prop_adultresp_outof_childutt ~ tokens_hr_child +
                                (1 | id),
                                data = chip_mm_en, REML = F)

m2_english_propresp_all <- lmer(prop_adultresp_outof_childutt ~ tokens_hr_child + activity +
                                (1 | id),
                                data = chip_mm_en, REML = F)

# see if adding the intx adds
anova(m1_english_propresp_all, m2_english_propresp_all)

# anova table for final model
anova(m2_english_propresp_all)



# emmeans
m2_english_propresp_all_emmeans_activity <- emmeans(m2_english_propresp_all, ~ activity)

m2_english_propresp_all_emmeans_activity
pairs(m2_english_propresp_all_emmeans_activity)


# plot
propresp_emmeans_en <- data.frame(emmeans(m2_english_propresp_all, ~ activity))


resp_en <- ggplot(propresp_emmeans_en, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent')) +
  labs(x = "", y = "EMM", title = "English - Proportion of Responses")


resp_en

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_english_propresp_all, type = "diag")
```



## PROP RESPONSES x ACTIVITY - SPANISH - ALL TALK
```{r}
# comparing models
m1_spanish_propresp_all <- lmer(prop_adultresp_outof_childutt ~ tokens_hr_child +
                                (1 | id),
                                data = chip_mm_sp, REML = F)

m2_spanish_propresp_all <- lmer(prop_adultresp_outof_childutt ~ tokens_hr_child + activity +
                                (1 | id),
                                data = chip_mm_sp, REML = F)

# see if adding the intx adds
anova(m1_spanish_propresp_all, m2_spanish_propresp_all)

# anova table for final model
anova(m2_spanish_propresp_all)



# emmeans
m2_spanish_propresp_all_emmeans_activity <- emmeans(m2_spanish_propresp_all, ~ activity)

m2_spanish_propresp_all_emmeans_activity
pairs(m2_spanish_propresp_all_emmeans_activity)


# plot
propresp_emmeans_sp <- data.frame(emmeans(m2_spanish_propresp_all, ~ activity))


resp_sp <- ggplot(propresp_emmeans_sp, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent')) +
  labs(x = "", y = "EMM", title = "Spanish - Proportion of Responses")


resp_sp

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_spanish_propresp_all, type = "diag")
```



## PROP IMIT/EXP x ACTIVITY - ENGLISH - ALL TALK; no sig main effect of activity
```{r}
# comparing models
m1_english_propimitexp_all <- lmer(prop_adult_imitexp_outof_childutt ~ tokens_hr_child +
                                (1 | id),
                                data = chip_mm_en, REML = F)

m2_english_propimitexp_all <- lmer(prop_adult_imitexp_outof_childutt ~ tokens_hr_child + activity +
                                (1 | id),
                                data = chip_mm_en, REML = F)

# see if adding the intx adds
anova(m1_english_propimitexp_all, m2_english_propimitexp_all)

# anova table for final model
anova(m2_english_propimitexp_all)


# emmeans
m2_english_propimitexp_all_emmeans_activity <- emmeans(m2_english_propimitexp_all, ~ activity)

m2_english_propimitexp_all_emmeans_activity


# plot
propimitexp_emmeans_en <- data.frame(emmeans(m2_english_propimitexp_all, ~ activity))

imit_exp_en <- ggplot(propimitexp_emmeans_en, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent')) +
  labs(x = "", y = "EMM", title = "English - Proportion of Imitations/Expansions")

imit_exp_en

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_english_propimitexp_all, type = "diag")
```



## PROP IMIT/EXP x ACTIVITY - SPANISH - ALL TALK; no sig main effect of activity
```{r}
# comparing models
m1_spanish_propimitexp_all <- lmer(prop_adult_imitexp_outof_childutt ~ tokens_hr_child +
                                (1 | id),
                                data = chip_mm_sp, REML = F)

m2_spanish_propimitexp_all <- lmer(prop_adult_imitexp_outof_childutt ~ tokens_hr_child + activity +
                                (1 | id),
                                data = chip_mm_sp, REML = F)

# see if adding the intx adds
anova(m1_spanish_propimitexp_all, m2_spanish_propimitexp_all)

# anova table for final model
anova(m2_spanish_propimitexp_all)


# emmeans
m2_spanish_propimitexp_all_emmeans_activity <- emmeans(m2_spanish_propimitexp_all, ~ activity)

m2_spanish_propimitexp_all_emmeans_activity


# plot
propimitexp_emmeans_sp <- data.frame(emmeans(m2_spanish_propimitexp_all, ~ activity))

imit_exp_sp <- ggplot(propimitexp_emmeans_sp, aes(activity, emmean, colour = activity)) + 
  geom_pointrange(aes(ymin = lower.CL, ymax = upper.CL),
                  position = position_dodge(width = 0.2), 
                  size = 1) +
  scale_color_manual(values=c("darkviolet", "firebrick1", "green2", "dodgerblue1", "darkgoldenrod1", "darkgrey")) + 
  theme(legend.position = "none",
        text = element_text(size = 20),
        axis.text.x = element_text(angle = 40, vjust = .9, hjust=.9)) +
  scale_x_discrete(labels = c('Books','Play', 'Food', 'Routines', 'Unst. Conv.', 'Adult-Cent')) +
  labs(x = "", y = "EMM", title = "Spanish - Proportion of Imitations/Expansions")

imit_exp_sp

# model diagnostics
# only takes into account fixed effects, not random effects
plot_model(m2_spanish_propimitexp_all, type = "diag")
```



# Combining plots
```{r}
# grid all
ggarrange(tokens_en, types_en, mlu_en, resp_en, imit_exp_en, common.legend = T, legend = "bottom")
ggarrange(tokens_sp, types_sp, mlu_sp, resp_sp, imit_exp_sp, common.legend = T, legend = "bottom")

```